---
title: "Clim_for_Crosses_Gardens"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Script for computing climate distance 

## Load libraries

```{r}
library(raster) #for the CV function 
library(tidyverse)

sem <- function(x, na.rm=FALSE) { #standard error function 
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 
```

## Load the pop and location data

```{r}
#pop info
pops_common_garden <- read_csv("../../parent_pops_common-gardens/input/WL2_Data/Pops_for_2023_WL2.csv") #pops included in common garden 
pops_common_garden_nonotes <- pops_common_garden %>% select(parent.pop:phylogroup, elevation.group) #subset columns

#Need to add YO1 for JGI:
yose1 <- tibble(parent.pop="YO1", phylogroup=NA) 
pops_common_garden_jgi <- bind_rows(pops_common_garden_nonotes, yose1)

#extra location info 
pop_loc <- read_csv("../input/Strep_tort_locs.csv")

#need to change YOSE to YO
pop_loc_yo <- pop_loc %>% mutate(parent.pop = str_replace(`Site code`, "YOSE(\\d+)", "YO\\1")) %>% select(Lat, Long, elev_m=`Elevation (m)`, parent.pop)

#merge in location info
pop_elev <- left_join(pops_common_garden_jgi, pop_loc_yo)

#add in common garden sites
sites_loc <- tibble(parent.pop=c("UCD_Garden", "WL2_Garden"), phylogroup=NA, Lat=c("38.53250", "38.82599"), Long=c("-121.78299", "-120.25090"), elev_m=c(16,2020))
pops_gardens_locs <- bind_rows(pop_elev, sites_loc)

#add row names
pops_gardens_locs_rowids <- pops_gardens_locs %>% 
  rowid_to_column() %>% 
  mutate(rowid = as.character(rowid))
```

## Extract WY 2025 from asc files
This is adapted from John's "Flint_Data_Extraction_from_Box.Rmd" code. 
Have to download the data (and unzip it) before running the below code chunks
Data is availalbe on the IntBio Box or online at https://www.sciencebase.gov/catalog/item/69fce794b66b010eddb81d1a 
```{r, eval=FALSE}
locs <- pops_gardens_locs_rowids %>% 
  rename(latitude = Lat, longitude = Long) %>% 
  # Make duplicate lat/long columns that will be transformed to match the Flint equal area projection
  mutate(latitude=as.numeric(latitude), 
         longitude=as.numeric(longitude)) %>% 
  mutate(latitude_aea = latitude,
         longitude_aea = longitude)

## define projection of flint data
flint_prj <- '+proj=aea +lat_1=34 +lat_2=40.5 +lat_0=0 +lon_0=-120 +x_0=0 +y_0=-4000000 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs' 

## Designate latitude and longitude columns as coordinates
coordinates(locs) <- ~longitude_aea + latitude_aea

## Define original projection (which is unprojected)
proj4string(locs) <- CRS("+proj=longlat +ellps=WGS84")

## Transform locations from original projection to be consistent with the flint data
locs_t <- spTransform(locs, CRS(flint_prj))
plot(locs_t)

## Make data frame from spatial points object, omit "optional" column
### This data frame has the original coordinates but also transformed coordinates
locs_p <- data.frame(locs_t) %>%
  dplyr::select(-optional)
```

### Extract asc values
```{r, eval=FALSE}
setwd("/Users/bqc/Library/Mobile Documents/com~apple~CloudDocs/Documents/UCDavis_Postdoc/crosses_common-gardens/input/Flint_WY2025/")

climate_variables <- c("aet", "cwd", "pck", "pet", 
                       "ppt", "tmn", "tmx")

path_name <- c("aet_WY2025","cwd_WY2025","pck_WY2025",
               "pet_WY2025","ppt_WY2025","tmn_WY2025","tmx_WY2025")
#path <- c("/Users/bqc/Library/Mobile Documents/com~apple~CloudDocs/Documents/UCDavis_Postdoc/crosses_common-gardens/input/Flint_WY2025/aet_WY2025") #for testing the code

# Month named vectors
months <- c("jan" = 1, "feb" = 2, "mar" = 3, "apr" = 4,
            "may" = 5, "jun" = 6, "jul" = 7, "aug" = 8,
            "sep" = 9, "oct" = 10, "nov" = 11, "dec" = 12)

walk(path_name, .progress = TRUE, .f = function(path) {
  # Extract variable name from path
  var_name <- str_extract(path, "[a-z]+(?=_WY2025)") #(?<=/) #for testing the code
  
  # Make list for all files pertaining to climate variable
  file_list <- list.files(path = path, pattern = ".asc", full.names = TRUE)
  
  # define a vector for populating pop column
  pops <- rep(locs$parent.pop, times = length(file_list))
  
  # create empty dataframe with pop, year, month, and each climate metric
  hist_clim <- data.frame(matrix(NA,
                                 nrow = length(pops),
                                 ncol = 5)) 
                         #ncol = vars: pop, year, month, var, var.data
  
  colnames(hist_clim) <- c("pop", "year", "month", "var", "var.data")
  
  hist_clim$pop <- pops
  hist_clim$var <- var_name
  
  # For loop filling in empty data frame
  # loop over files
  for (j in 1:length(file_list)) {
    # loop over rows of hist_clim to populate the dataframe
    file_name <- basename(file_list[j]) # Lose the directory names
    dec_file_name <- sub('.gz$', '', file_list[j], fixed = TRUE)
    # Can do following due to uniform naming scheme
    hist_clim[((j - 1) * nrow(locs_p) + 1):(j * nrow(locs_p)), 5] <-
        raster::extract(raster(dec_file_name), locs_t)
    hist_clim[((j - 1) * nrow(locs_p) + 1):(j * nrow(locs_p)), 3] <-
      months[[str_sub(file_name, 8, 10)]]
    hist_clim[((j - 1) * nrow(locs_p) + 1):(j * nrow(locs_p)), 2] <-
      as.numeric(str_sub(file_name, 4, 7))
    file.remove(dec_file_name)
  }

# Sort the data frame
  hist_clim <- arrange(hist_clim, year, month)
  
# Save the data frame
  new_file_name <- paste0("Test_", var_name, "_WY2025.csv")
  write.csv(hist_clim, new_file_name, row.names = FALSE)
})
```

### Merge
```{r, eval=FALSE}
setwd("/Users/bqc/Library/Mobile Documents/com~apple~CloudDocs/Documents/UCDavis_Postdoc/crosses_common-gardens/input/Flint_WY2025/")
file_list <- list.files(pattern = "_WY2025.csv", full.names = TRUE)
all_climate <- map(file_list, read_csv)
all_climate <- reduce(all_climate, bind_rows) 
head(all_climate)
all_climate <- all_climate %>% pivot_wider(names_from = var, values_from = var.data)
write_csv(all_climate, "Flint_All_WY2025.csv")
```

## Load raw flint data for water years prior to 2025

```{r}
flint_data1 <- read_csv("../input/Updated_Flint_Climate_Oct2024.csv") #This only goes through Aug 2024
flint_data2 <- read_csv("../input/Updated_Flint_Sept-Dec2024.csv") #Sept-Dec 2024

#merge:
flint_data <- bind_rows(flint_data1, flint_data2)
```

## Convert raw flint into a workable format (original code in "Climate_Shapefile.Rmd")

```{r}
cwd <- flint_data %>% filter(str_detect(DataFileName, "cwd"))
cwd_long <- cwd %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "cwd") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, cwd)

pet <- flint_data %>% filter(str_detect(DataFileName, "pet"))
pet_long <- pet %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "pet") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, pet)

aet <- flint_data %>% 
  filter(str_detect(DataFileName, "aet"))
aet_long <- aet %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "aet") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, aet)

pck <- flint_data %>% filter(str_detect(DataFileName, "pck"))
pck_long <- pck %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "pck") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, pck)

ppt <- flint_data %>% filter(str_detect(DataFileName, "ppt"))
ppt_long <- ppt %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "ppt") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, ppt)

tmn <- flint_data %>% filter(str_detect(DataFileName, "tmn"))
tmn_long <- tmn %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "tmn") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, tmn)

tmx <- flint_data %>% filter(str_detect(DataFileName, "tmx"))
tmx_long <- tmx %>% 
  pivot_longer(!DataFileName, names_to = "rowid", values_to = "tmx") %>% 
  extract(DataFileName, c("year", "month"), "(\\d+)(.*)", convert = TRUE) %>% 
  separate(month, into = c("month", "file_type")) %>% select(rowid, year, month, tmx)

#merge:
flint_long <- full_join(aet_long, cwd_long)
flint_long <- full_join(flint_long, pck_long)
flint_long <- full_join(flint_long, pet_long)
flint_long <- full_join(flint_long, ppt_long)
flint_long <- full_join(flint_long, tmn_long)
flint_long <- full_join(flint_long, tmx_long)

flint_pops <- full_join(pops_gardens_locs_rowids, flint_long) 
```

Note: flint_pops includes the 2 common garden sites and pops not grown in crosses gardens 

### Merge pre and post 2025 flint data
```{r}
all_climate <- read_csv("../input/Flint_WY2025/Flint_All_WY2025.csv")
all_climate_pops <- all_climate %>% 
  rename(parent.pop=pop) %>% 
  left_join(pops_gardens_locs_rowids) %>% 
  mutate(month=month(month, label = TRUE, abbr = TRUE)) %>% #convert from nums to char names 
  mutate(month=as.character(month),
         month=tolower(month)) %>% 
  filter(year!="2024") #remove 2024 so no repeats with flint_pops
  

all_flint_pops <- bind_rows(flint_pops, all_climate_pops)
head(all_flint_pops)
```

### Subset to only the 10 pops plus the garden sites

TM2, WL2, LV1, SQ3, WL1, YO11, BH, CC, DPR, WV

```{r}
crosses_parents <- c("TM2", "WL2", "LV1", "SQ3", "WL1", "YO11", "BH", "CC", "DPR", "WV")

pop_elev_climate <- all_flint_pops %>% 
  select(parent.pop, elevation.group, elev_m, Lat:Long, year:tmx) %>% #organize the columns 
  mutate(elevation.group=if_else(parent.pop=="UCD_Garden", "Low",  #add elevation group for gardens
                                 if_else(parent.pop=="WL2_Garden", "High", elevation.group))) %>% 
  filter(parent.pop %in% crosses_parents | str_detect(parent.pop, "Garden")) 

unique(pop_elev_climate$parent.pop) #check that filtering worked 
```

## Flint Water Year (Nov-Oct)

```{r}
month_nums <- tibble(month=c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec"),
                     month_nums=c(1:12)) #give calendar months a number 

#merge:
flint_all_year_mosnums <- left_join(pop_elev_climate, month_nums) %>% arrange(parent.pop, year, month_nums) 

#define the water year as November-October:
flint_all_year_wtr_yr <- flint_all_year_mosnums %>% 
  mutate(wtr_yr = year + month_nums %in% c(11:12)) %>% 
  mutate(timeframe = case_when(
                                wtr_yr < 1965 ~ "beforehistoric",
                                wtr_yr >= 1965 & wtr_yr < 1995 ~ "historic",
                                wtr_yr >= 1995 & wtr_yr <= 2025 ~ "recent")) %>%
                         mutate(timeframe = as.factor(timeframe), month = as.factor(month)) %>%
                         filter(wtr_yr != 1895) %>% #remove years with less than 12 months of data 
                         mutate(months_wtryr = case_when(
                           month == "nov" ~ 1,
                           month == "dec" ~ 2,
                           month == "jan" ~ 3,
                           month == "feb" ~ 4,
                           month == "mar" ~ 5,
                           month == "apr" ~ 6,
                           month == "may" ~ 7, 
                           month == "jun" ~ 8,
                           month == "jul" ~ 9, 
                           month == "aug" ~ 10,
                           month == "sep" ~ 11,
                           month == "oct" ~ 12 )) %>% 
  select(parent.pop:month, timeframe, wtr_yr, months_wtryr, aet:tmx)  #organize the columns 
summary(flint_all_year_wtr_yr)

#water year is calculated Nov - October to match census dates at WL2. Could have issues with this, but move forward for now. Can be changed later. 
##Note: we don't currently have Oct for 2025!
```

## Bioclim water year calculations

Referenced this r code: <https://github.com/rspatial/dismo/blob/master/R/biovars.R>

```{r}
# Calculating average temp and diurnal range for each month
bioclim_wtr_yr_prep <- flint_all_year_wtr_yr %>% 
  mutate(tavg = (tmn + tmx)/2, t_diurnal = (tmx-tmn))

#Bio 1, 2, 4, 7, 12, 15
bioclim_wtr_yr_calc <- bioclim_wtr_yr_prep %>% 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ann_tmean=mean(tavg),  #Bio1 - Annual Mean Temperature
            mean_diurnal_range=mean(t_diurnal), #Bio2 - Mean Diurnal Range
            temp_seasonality=sd(tavg), #Bio4 - Temperature Seasonality
            temp_ann_range=(max(tmx))-(min(tmn)), #bio7 - temp annual range
            ann_ppt=sum(ppt), #bio12 - annual precip
            ppt_seasonality=cv(ppt+1)) #bio15 - Precipitation Seasonality (+1 to avoid strange CVs for areas where mean rainfaill is < 1)

# Calculating wettest, driest, warmest, and coldest months 
wettest_month <- bioclim_wtr_yr_prep %>%  #there's one wettest month per pop/year
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_max(ppt)
driest_month <- bioclim_wtr_yr_prep %>%  #there's more than one driest month for some pops and years 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_min(ppt)
warmest_month <- bioclim_wtr_yr_prep %>% #there's more than one warmest month for 1 pop/year
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_max(tavg)
coldest_month <- bioclim_wtr_yr_prep %>% #there's more than one driest month for some pops and years 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_min(tavg)

# Bio 8, 9, 18, 19
bio8_wtryr <- wettest_month %>% #bio8 = tmean_wettest_month
  dplyr::select(parent.pop, elevation.group, elev_m, timeframe, wtr_yr, tmean_wettest_month=tavg)
bio9_wtryr <- driest_month %>% #bio9 = tmean_driest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(tmean_driest_month=mean(tavg)) #taking the average b/c some years where there are multiple driest months 
bio18_wtryr <- warmest_month %>% #bio18 = ppt_warmest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ppt_warmest_month=mean(ppt)) #taking the avg b/c more than one warmest month for one pop/year
bio19_wtryr <- coldest_month %>% #bio19 = ppt_coldest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ppt_coldest_month=mean(ppt)) #taking the avg b/c more than one coldest month for one pop/year
#merge:
bio8_9_wtryr <- full_join(bio8_wtryr, bio9_wtryr) 
bio18_19_wtryr <- full_join(bio18_wtryr, bio19_wtryr) 
all_periods_wtryr <- full_join(bio8_9_wtryr, bio18_19_wtryr)

#Merge all bioclims
bioclim_wtryr <- full_join(bioclim_wtr_yr_calc, all_periods_wtryr)
summary(bioclim_wtryr)
```

Note: bioclim_wtryr includes the 2 common garden sites

## Merge Flint and Bioclim
```{r}
#summarize flint by year to merge it with the bioclim data
flint_yrly_avgs_wtr_yr <- flint_all_year_wtr_yr %>% 
  filter(timeframe!="beforehistoric") %>% 
  rename(year=wtr_yr, year_cal=year) %>% 
  group_by(parent.pop, elevation.group, elev_m, Lat, Long, timeframe, year) %>% 
  summarise_at(c("cwd", "pck", "ppt", "tmn", "tmx"), c(mean), na.rm = TRUE)

#subset bioclim water year
bioclim_wtryr_to_merge <- bioclim_wtryr %>% 
  filter(timeframe!="beforehistoric") %>% 
  rename(year=wtr_yr) 

#merge
wtr_yr_clim <- left_join(flint_yrly_avgs_wtr_yr, bioclim_wtryr_to_merge) %>% 
  mutate(Season="Water Year")
write_csv(wtr_yr_clim, "../output/Climate/WtrYr_Clim_2025NoOct.csv")
```

## Flint Water Year (Oct-Sep)

```{r}
#define the water year as Octover-Sept:
flint_all_year_wtr_yr_trad <- flint_all_year_mosnums %>% 
  mutate(wtr_yr = year + month_nums %in% c(10:12)) %>% 
  mutate(timeframe = case_when(
                                wtr_yr < 1965 ~ "beforehistoric",
                                wtr_yr >= 1965 & wtr_yr < 1995 ~ "historic",
                                wtr_yr >= 1995 & wtr_yr <= 2025 ~ "recent")) %>%
                         mutate(timeframe = as.factor(timeframe), month = as.factor(month)) %>%
                         filter(wtr_yr != 1895) %>% #remove years with less than 12 months of data 
                         mutate(months_wtryr = case_when(
                           month == "oct" ~ 1,
                           month == "nov" ~ 2,
                           month == "dec" ~ 3,
                           month == "jan" ~ 4,
                           month == "feb" ~ 5,
                           month == "mar" ~ 6,
                           month == "apr" ~ 7,
                           month == "may" ~ 8, 
                           month == "jun" ~ 9,
                           month == "jul" ~ 10, 
                           month == "aug" ~ 11,
                           month == "sep" ~ 12)) %>% 
  select(parent.pop:month, timeframe, wtr_yr, months_wtryr, aet:tmx)  #organize the columns 
summary(flint_all_year_wtr_yr_trad)

#water year is calculated Nov - October to match census dates at WL2. Could have issues with this, but move forward for now. Can be changed later. 
##Note: we don't currently have Oct for 2025!
```

## Bioclim water year calculations

Referenced this r code: <https://github.com/rspatial/dismo/blob/master/R/biovars.R>

```{r}
# Calculating average temp and diurnal range for each month
bioclim_wtr_yr_trad_prep <- flint_all_year_wtr_yr_trad %>% 
  mutate(tavg = (tmn + tmx)/2, t_diurnal = (tmx-tmn))

#Bio 1, 2, 4, 7, 12, 15
bioclim_wtr_yr_trad_calc <- bioclim_wtr_yr_trad_prep %>% 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ann_tmean=mean(tavg),  #Bio1 - Annual Mean Temperature
            mean_diurnal_range=mean(t_diurnal), #Bio2 - Mean Diurnal Range
            temp_seasonality=sd(tavg), #Bio4 - Temperature Seasonality
            temp_ann_range=(max(tmx))-(min(tmn)), #bio7 - temp annual range
            ann_ppt=sum(ppt), #bio12 - annual precip
            ppt_seasonality=cv(ppt+1)) #bio15 - Precipitation Seasonality (+1 to avoid strange CVs for areas where mean rainfaill is < 1)

# Calculating wettest, driest, warmest, and coldest months 
wettest_month_trad <- bioclim_wtr_yr_trad_prep %>%  #there's one wettest month per pop/year
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_max(ppt)
driest_month_trad <- bioclim_wtr_yr_trad_prep %>%  #there's more than one driest month for some pops and years 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_min(ppt)
warmest_month_trad <- bioclim_wtr_yr_trad_prep %>% #there's more than one warmest month for 1 pop/year
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_max(tavg)
coldest_month_trad <- bioclim_wtr_yr_trad_prep %>% #there's more than one driest month for some pops and years 
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  slice_min(tavg)

# Bio 8, 9, 18, 19
bio8_wtryr_trad <- wettest_month_trad %>% #bio8 = tmean_wettest_month
  dplyr::select(parent.pop, elevation.group, elev_m, timeframe, wtr_yr, tmean_wettest_month=tavg)
bio9_wtryr_trad <- driest_month_trad %>% #bio9 = tmean_driest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(tmean_driest_month=mean(tavg)) #taking the average b/c some years where there are multiple driest months 
bio18_wtryr_trad <- warmest_month_trad %>% #bio18 = ppt_warmest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ppt_warmest_month=mean(ppt)) #taking the avg b/c more than one warmest month for one pop/year
bio19_wtryr_trad <- coldest_month_trad %>% #bio19 = ppt_coldest_month
  group_by(parent.pop, elevation.group, elev_m, timeframe, wtr_yr) %>% 
  summarise(ppt_coldest_month=mean(ppt)) #taking the avg b/c more than one coldest month for one pop/year
#merge:
bio8_9_wtryr_trad <- full_join(bio8_wtryr_trad, bio9_wtryr_trad) 
bio18_19_wtryr_trad <- full_join(bio18_wtryr_trad, bio19_wtryr_trad) 
all_periods_wtryr_trad <- full_join(bio8_9_wtryr_trad, bio18_19_wtryr_trad)

#Merge all bioclims
bioclim_wtryr_trad <- full_join(bioclim_wtr_yr_trad_calc, all_periods_wtryr_trad)
summary(bioclim_wtryr_trad)
```

Note: bioclim_wtryr includes the 2 common garden sites

## Merge Flint and Bioclim
```{r}
#summarize flint by year to merge it with the bioclim data
flint_yrly_avgs_wtr_yr_trad <- flint_all_year_wtr_yr_trad %>% 
  filter(timeframe!="beforehistoric") %>% 
  rename(year=wtr_yr, year_cal=year) %>% 
  group_by(parent.pop, elevation.group, elev_m, Lat, Long, timeframe, year) %>% 
  summarise_at(c("cwd", "pck", "ppt", "tmn", "tmx"), c(mean), na.rm = TRUE)

#subset bioclim water year
bioclim_wtryr_trad_to_merge <- bioclim_wtryr_trad %>% 
  filter(timeframe!="beforehistoric") %>% 
  rename(year=wtr_yr) 

#merge
wtr_yr_clim_trad <- left_join(flint_yrly_avgs_wtr_yr_trad, bioclim_wtryr_trad_to_merge) %>% 
  mutate(Season="Water Year")
write_csv(wtr_yr_clim_trad, "../output/Climate/WtrYr_Clim_2025TradWtrYr.csv")

flint_all_year_wtr_yr_trad %>% filter(wtr_yr==2025)
```