---
title: "Plasticity_SampleSizes"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figuring out sample sizes for potential plasticity analysis

Potential Analyses:

-   Size post-establishment

-   Size at rep

-   Growth rate

-   Physiology?

-   Changes in above traits (plasticity) --\>/correspond with diffs in fitness?

## Libraries

```{r}
library(tidyverse)
```

## WL2 data

### 2023
```{r}
wl2_mortpheno_2023 <- read_csv("../../parent_pops_common-gardens/input/WL2_Data/CorrectedCSVs/WL2_mort_pheno_20231020_corrected.csv")

wl2_mortpheno_2023_pops <- wl2_mortpheno_2023 %>% 
  select(block:rep, death.date) %>% 
  filter(pop!="buffer") %>% 
  filter(!str_detect(pop, "\\*")) %>% 
  mutate(pop=str_replace(pop, "0", "O")) %>% 
  mutate(mf=as.numeric(mf))

wl2_2023_est <- wl2_mortpheno_2023_pops %>% 
  mutate(death.date=mdy(death.date)) %>% 
  filter(death.date > "2023-08-10" | is.na(death.date)) #only keep indivs that established

wl2_2023_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

### 2024
```{r}
wl2_mortpheno_2024 <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_mort_pheno_20241023_corrected.csv")
wl2_pop_info_2024 <- read_csv("../input/WL2_2024_Data/Final_2023_2024_Pop_Loc_Info.csv") %>% 
  select(Pop.Type:unique.ID) %>% 
  rename(row=bedrow, col=bedcol)

wl2_mortpheno_2024_pops <- wl2_mortpheno_2024 %>% 
  select(bed:unique.ID, death.date, missing.date) %>% 
  left_join(wl2_pop_info_2024) %>% 
  filter(unique.ID!="buffer") %>% 
  filter(Pop.Type!="2023-TM2-fruit", Pop.Type!="2023-survivor") #keep only 2024 plants 

wl2_2024_est <- wl2_mortpheno_2024_pops %>% 
  mutate(death.date=mdy(death.date), missing.date=mdy(missing.date)) %>% 
  filter(death.date > "2024-07-06" | is.na(death.date))

wl2_2024_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

### 2025
```{r}
wl2_mortpheno_2025 <- read_csv("../input/WL2_2025_Data/CorrectedCSVs/WL2_mort_pheno_20250929_corrected.csv")
wl2_pop_info_2025 <- read_csv("../input/WL2_2025_Data/2025_Pop_Loc_Info Updated.csv") %>% 
  select(status:Unique.ID)

wl2_mortpheno_2025_pops <- wl2_mortpheno_2025 %>% 
  select(bed:Unique.ID, bud.date, death.date, survey.notes) %>% 
  left_join(wl2_pop_info_2025) %>% 
  filter(Unique.ID!="buffer", !is.na(Unique.ID)) %>% 
  filter(status=="available") %>% #only keep plants planted in 2025
  mutate(Pop.Type=if_else(str_detect(pop.id, "\\) x"), "F2",
                          if_else(str_detect(pop.id, "x"), "F1",
                                  "Parent"
                          ))) #define different pop types 

wl2_2025_est <- wl2_mortpheno_2025_pops %>% 
  mutate(deadatplanting = if_else(is.na(survey.notes), NA,
                                  if_else(survey.notes=="dead pre-planting" | 
                                            survey.notes=="dead at planting",
                                          "Yes", NA))) %>% 
  filter(is.na(deadatplanting)) %>% #remove plants that were dead at planting 
  select(-status, -deadatplanting, -survey.notes) %>% #remove unnecessary cols 
  mutate(death.date=mdy(death.date)) %>% #convert to date format 
  filter(death.date > "2025-06-21" | is.na(death.date))

wl2_2025_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

### 2026
```{r}
wl2_mortpheno_2026 <- read_csv("../input/WL2_2026_Data/CorrectedCSVs/WL2_mort_pheno_20260724_corrected.csv") %>% filter(Unique.ID!="buffer")
wl2_pop_info_2026 <- read_csv("../input/WL2_2026_Data/Buffer New Bed Map_Corrected.csv") %>% 
  select(pop.id:Rep, status, Type, Unique.ID) %>% filter(Unique.ID!="buffer")

wl2_mortpheno_2026_pops <- wl2_mortpheno_2026 %>% 
  select(Unique.ID, death.date, survey.notes) %>% 
  left_join(wl2_pop_info_2026) %>% 
  filter(!is.na(Unique.ID)) %>% 
  filter(status=="available") #only keep plants planted in 2026

wl2_2026_est <- wl2_mortpheno_2026_pops %>% 
  filter(!str_detect(survey.notes, "dead at planting")) %>% 
  select(-survey.notes, -status) %>% 
  mutate(death.date=mdy(death.date)) %>% 
  filter(death.date > "2026-06-12" | is.na(death.date))

wl2_2026_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

## UCD data

### 2023
```{r}
ucd_mortpheno_2023 <- read_csv("../../parent_pops_common-gardens/input/UCD_Data/CorrectedCSVs/UCD_transplants_pheno_mort_20231016_corrected.csv") 

ucd_mortpheno_2023_pops <- ucd_mortpheno_2023 %>% 
  select(block:rep, death.date=`Death Date`) %>% 
  filter(pop!="buffer") %>% 
  filter(rep != 100) #get rid of individuals that germinated in the field  

ucd_2023_est <- ucd_mortpheno_2023_pops %>% 
  mutate(death.date=mdy(death.date)) %>% 
  filter(death.date > "2022-12-24" | is.na(death.date)) #keep indivs that established

ucd_2023_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

### 2024
```{r}
ucd_mortpheno_2024 <- read_csv("../input/UCD2023_2024_Data/CorrectedCSVs/UCD_mort_pheno_20241108_corrected.csv") 
ucd_pop_info_2024 <- read_csv("../input/UCD2023_2024_Data/Genotypes_2023_2024.csv") %>%
  rename(col=column)

ucd_mortpheno_2024_pops <- ucd_mortpheno_2024 %>% 
  mutate(unique.ID=as.numeric(unique.ID)) %>% 
  select(bed:unique.ID, death.date, missing.date) %>% 
  left_join(ucd_pop_info_2024) %>% 
  filter(unique.ID!="buffer") %>% 
  filter(unique.ID!=2032) %>%  #REMOVE PLANT 2032 (BED F-39-A) - MULTIPLE PLANTS WERE GROWING IN THAT SPOT. 
  mutate(pop.id=if_else(str_detect(pop.id, "WL2-"), "WL2",
                        if_else(str_detect(pop.id, "TM2-"), "TM2",
                                pop.id))) #remove mf from pop name of WL2 and TM2 plants 

ucd_2024_est <- ucd_mortpheno_2024_pops %>% 
  mutate(death.date=mdy(death.date), missing.date=mdy(missing.date)) %>% 
  filter(death.date > "2023-12-29" | is.na(death.date))

ucd_2024_est %>% 
  ggplot(aes(death.date)) +
  geom_histogram()
```

## Summaries
```{r}
wl2_2023_popmfs <- wl2_2023_est %>% 
  group_by(pop, mf) %>% 
  summarise(WL2_2023=n()) %>% 
  filter(WL2_2023>2) #remove pop-mf combos with few indivs
unique(wl2_2023_est$pop) #22 pops with establishment 

wl2_2024_pops <- wl2_2024_est %>% 
  group_by(Pop.Type, pop) %>% 
  summarise(WL2_2024=n()) %>% 
  filter(WL2_2024>2) #remove pops/crosses with few indivs
wl2_2024_est %>% filter(Pop.Type=="Parent") %>% select(pop) %>% distinct() %>% pull() #10 parent pops with establishment (only planted 10 starting this year)

wl2_2025_popmfs <- wl2_2025_est %>% 
  rename(pop=pop.id) %>% 
  group_by(Pop.Type, pop, mf) %>% 
  summarise(WL2_2025=n()) %>% 
  filter(WL2_2025>2) #remove pop-mf combos with few indivs
wl2_2025_est %>% filter(Pop.Type=="Parent") %>% select(pop.id) %>% distinct() %>% pull() #10 parent pops with establishment

ucd_2023_popmfs <- ucd_2023_est %>% 
  group_by(pop, mf) %>% 
  summarise(UCD_2023=n()) %>% 
  filter(UCD_2023>2) #remove pop-mf combos with few indivs
unique(ucd_2023_est$pop) #23 pops with establishment 

ucd_2024_popmfs <- ucd_2024_est %>% 
  rename(pop=pop.id, Pop.Type=`Plant Type`) %>% 
  group_by(Pop.Type, pop, mf) %>% 
  summarise(UCD_2024=n()) %>% 
  filter(UCD_2024>2) #remove pop-mf combos with few indivs
ucd_2024_est %>% filter(str_detect(`Plant Type`, "Parent")) %>% select(pop.id) %>% distinct() %>% pull() #10 parent pops with establishment
```

## Spatial Plasticity

### 2023 WL2 vs. 2023 UCD (Pops and mfs)

```{r}
wl2_ucd_2023 <- wl2_2023_popmfs %>% 
  left_join(ucd_2023_popmfs) %>% 
  filter(!is.na(UCD_2023)) #only keep pop/mfs with match at UCD
dim(wl2_ucd_2023) #52 pop/mfs
unique(wl2_ucd_2023$pop) #19 pops 

wl2_ucd_2023 %>% 
  group_by(pop) %>% 
  summarise(TotalMfs=n()) %>% 
  arrange(TotalMfs)
```

### 2023 WL2 vs. 2024 UCD (Pops and mfs)

```{r}
wl2_2023_ucd_2024 <- wl2_2023_popmfs %>% 
  left_join(ucd_2024_popmfs) %>% 
  filter(!is.na(UCD_2024)) %>% 
  select(-Pop.Type)
dim(wl2_2023_ucd_2024) #24 pop/mfs
unique(wl2_2023_ucd_2024$pop) #7 pops 

wl2_2023_ucd_2024 %>% 
  group_by(pop) %>% 
  summarise(TotalMfs=n()) %>% 
  arrange(TotalMfs)
```

### 2024 WL2 vs. 2024 UCD (Pops only)

```{r}
ucd_2024_popmfs_prep <- ucd_2024_est %>% 
  rename(pop=pop.id, Pop.Type=`Plant Type`) %>% 
  mutate(Pop.Type=if_else(str_detect(Pop.Type, "Parent"), "Parent", 
                          Pop.Type)) %>% #change to match wl2_2024
  group_by(Pop.Type, pop) %>% #don't group by mf since no mf for wl2_2024 
  summarise(UCD_2024=n()) %>% 
  filter(UCD_2024>2) 

wl2_ucd_2024 <- wl2_2024_pops %>% 
  left_join(ucd_2024_popmfs_prep) %>% 
  filter(!is.na(UCD_2024)) 
dim(wl2_ucd_2024) #45 pops/cross types 

wl2_ucd_2024 %>% 
  group_by(Pop.Type) %>% 
  summarise(Total=n()) #7 parent pops, 6 F1s, 3 F2s 
```

### 2025 WL2 vs. 2024 UCD (Pops and mfs)

```{r}
wl2_2025_popmfs_prep <- 
  wl2_2025_est %>% 
  rename(pop=pop.id) %>% 
  mutate(mf=if_else(Pop.Type=="Parent", mf, 
                    NA)) %>% #only keep mfs for parents since that's the mf info we have for ucd_2024
  group_by(Pop.Type, pop, mf) %>% 
  summarise(WL2_2025=n()) %>% 
  filter(WL2_2025>2) %>% 
  mutate(mf=as.numeric(mf))

wl2_2025_ucd_2024 <- wl2_2025_popmfs_prep %>% 
  left_join(ucd_2024_popmfs, join_by(pop,mf)) %>% 
  filter(!is.na(UCD_2024)) %>% 
  select(Pop.Type=Pop.Type.x, pop:WL2_2025, UCD_2024)
dim(wl2_2025_ucd_2024) #20 pops/cross types 

wl2_2025_ucd_2024 %>% 
  group_by(Pop.Type) %>% 
  summarise(Total=n()) #9 F1s 
wl2_2025_ucd_2024 %>% filter(Pop.Type=="Parent") %>% select(pop) %>% distinct() %>% pull() #4 parent pops 
```

### 2026 WL2 vs. 2024 UCD (Pops and mfs)

```{r}

```

## Temporal Plasticity

### UCD: 2023, 2024 (Pops and mfs)

```{r}

```

### WL2: 2023, 2024 (pops only), 2025, 2026

```{r}

```
