---
title: "UCD_2024_TotalFitness"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Total Fitness for UCD 2023-2024 Garden

Will need to add fruit+seed mass once it's measured for all plants

## Libraries

```{r}
library(tidyverse)

sem <- function(x, na.rm=FALSE) {  #for calculating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 
```

## Read in data
```{r}
ucd_surv <- read_csv("../input/UCD2023_2024_Data/CorrectedCSVs/UCD_mort_pheno_20241108_corrected.csv")

ucd_biomass <- read_csv("../input/UCD2023_2024_Data/CorrectedCSVs/UCD_Biomass_20250723_corrected.csv") %>% 
  mutate(unique.ID=as.character(unique.ID))
```

## Pop Info
```{r}
ucd_popinfo <- read_csv("../input/UCD2023_2024_Data/Genotypes_2023_2024.csv") %>% 
  mutate(unique.ID=as.character(unique.ID))
```

### Biomass Merge for fruit+seed mass measurements 
```{r}
ucd_biomass_blocks <- ucd_biomass %>% 
  left_join(ucd_popinfo) %>% 
  select(block, unique.ID, date.collected, date.meas, total.biomass_g, total.seed.mass_g, survey.notes)
write_csv(ucd_biomass_blocks, "../output/UCD_Traits/Biomass_Blocks.csv")
```

## Elevation Info / Climate distance
```{r}
ucd_clim_dist <- read_csv("../output/Climate/UCD_2024_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
head(ucd_clim_dist)

ucd_clim_dist_wide <- ucd_clim_dist %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop.id=parent.pop)
```

## Combine all fitness metrics
```{r}
ucd_totalfit <- ucd_surv %>% 
  filter(!is.na(unique.ID), unique.ID!="buffer") %>% 
  filter(is.na(missing.date)) %>% #remove plants that went missing (usually caused by crows)
  filter(survey.notes!="dead at planting"|is.na(survey.notes)) %>% #remove plants that were dead at planting 
  mutate(death.date=mdy(death.date), bud.date=mdy(bud.date)) %>% 
  mutate(Establishment = if_else(is.na(death.date), 1, 
                                 if_else(death.date < "2023-12-29", 0, 1)),
         SurvtoBud = if_else(!is.na(bud.date), 1, 0)) %>% 
  select(bed:bud.date, death.date, Establishment, SurvtoBud) %>% 
  left_join(ucd_biomass) %>% 
  select(-date.collected, -person.meas, -date.meas, -total.seed.mass_g, -survey.notes) %>% 
  left_join(ucd_popinfo) %>% 
  select(-rack, -column) %>% 
  rename(Pop.Type=`Plant Type`) %>% 
  mutate(Pop.Type=if_else(str_detect(Pop.Type, "Parent"), "Parent", Pop.Type)) %>% 
  mutate(pop.id=if_else(str_detect(pop.id, "WL2-"), "WL2",
                        if_else(str_detect(pop.id, "TM2-"), "TM2",
                                pop.id))) #remove mf from pop name of WL2 and TM2 plants 
```

## Means
```{r}
ucd_totalfit_summary <- ucd_totalfit %>% 
  group_by(Pop.Type, pop.id) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanBiomass=mean(total.biomass_g, na.rm=TRUE), semBiomass=sem(total.biomass_g, na.rm = TRUE))

ucd_totalfit_summary

ucd_totalfit %>% filter(SurvtoBud==1, is.na(total.biomass_g)) #quite a few plants that survived to rep that we don't have biomass for... should investigate 
```

## Quick Figures

### Establishment
```{r}
ucd_totalfit_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  left_join(ucd_clim_dist_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanEst), y=meanEst, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Establishment", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

ucd_totalfit_summary %>% 
  filter(Pop.Type=="F1") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanEst), y=meanEst)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Establishment")


ucd_totalfit_summary %>% 
  filter(Pop.Type=="F2") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanEst), y=meanEst)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Establishment")
```
Establishment was pretty high overall

### Surv to Bud
```{r}
ucd_totalfit_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  left_join(ucd_clim_dist_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanSurvtoBud), y=meanSurvtoBud, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Surv to Budding", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

ucd_totalfit_summary %>% 
  filter(Pop.Type=="F1") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanSurvtoBud), y=meanSurvtoBud)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Surv to Budding")


ucd_totalfit_summary %>% 
  filter(Pop.Type=="F2") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanSurvtoBud), y=meanSurvtoBud)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Surv to Budding")
```
Potentially some hybrid vigor in both F1s and F2s? Seem to have higher survival to rep than parent pops (esp high elev parent pops)

### Biomass 
```{r}
ucd_totalfit_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  filter(!is.na(meanBiomass)) %>% 
  left_join(ucd_clim_dist_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanBiomass), y=meanBiomass, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanBiomass-semBiomass,
                    ymax=meanBiomass+semBiomass),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Biomass (g)", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()
ucd_totalfit %>% filter(pop.id=="BH") #3 BH survived to budding, but we only have biomass for one of them...

ucd_totalfit_summary %>% 
  filter(Pop.Type=="F1") %>% 
  filter(!is.na(meanBiomass)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanBiomass), y=meanBiomass)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanBiomass-semBiomass,
                    ymax=meanBiomass+semBiomass),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Biomass (g)")


ucd_totalfit_summary %>% 
  filter(Pop.Type=="F2") %>% 
  filter(!is.na(meanBiomass)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanBiomass), y=meanBiomass)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanBiomass-semBiomass,
                    ymax=meanBiomass+semBiomass),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Biomass (g)")
```