---
title: "WL2_InitialSize_Establishment"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

# Checking the effects of initial size on establishment probability

Establishment = survival first 3 weeks post transplant

To Do:

-   Plot the model predictions - easier to interpret than population averages

-   Analyze parent pops, F1s (put the two parents as random effects), F2s separately

    -   First try one pool is parents and the others is crosses

-   What fraction of the plants are at the “good” size at week 3?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r}
library(tidyverse)
library(lme4)
```

## Load Initial Size

```{r}
initial_size <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_Initial_DNA_size_survey_20240607_corrected.csv") %>% 
  mutate(unique.ID=as.character(unique.ID)) %>% 
  select(unique.ID:long.leaf.cm)
head(initial_size)
```

## Load Survival

```{r}
wl2_surv <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_mort_pheno_20241023_corrected.csv") %>% 
  select(block:unique.ID, death.date, missing.date, survey.notes)
head(wl2_surv)
```

## Load pop info

```{r}
pop_info <- read_csv("../input/WL2_2024_Data/Final_2023_2024_Pop_Loc_Info.csv") %>% 
  select(Pop.Type:bed, row=bedrow, col=bedcol, pop:unique.ID)

unique(pop_info$Pop.Type)
unique(pop_info$status)
```

## Merge

```{r}
size_surv <- left_join(wl2_surv, initial_size)

size_surv_pops <- left_join(pop_info, size_surv)

size_surv_2024pops <- size_surv_pops %>% filter(Pop.Type != "2023-TM2-fruit", Pop.Type != "2023-survivor")
unique(size_surv_2024pops$death.date)
unique(size_surv_2024pops$missing.date)
```

## Establishment

```{r}
establishment <- size_surv_2024pops %>% 
  mutate(Est_Surv=if_else(is.na(death.date), 1, 
                          if_else(death.date=="6/18/24" | death.date=="6/25/24" | death.date=="7/2/24", 0,
                                       1))) %>% 
  mutate(Est_Surv = if_else(is.na(missing.date), Est_Surv, 
                            if_else(missing.date=="6/25/24", 0, Est_Surv)))

head(establishment)

establishment %>% filter(missing.date=="6/25/24") #double check it gave 0s to ones that went missing 
```

## Quick Plots

```{r}
establishment %>% 
  ggplot(aes(`hypocotyl. length.cm`, Est_Surv)) +
  geom_point()

establishment %>% 
  ggplot(aes(height.cm, Est_Surv)) +
  geom_point()

establishment %>% 
  ggplot(aes(long.leaf.cm, Est_Surv)) +
  geom_point()
```

## PopType Averages

```{r}
est_summary <- establishment %>% 
  group_by(Pop.Type) %>% 
  summarise(meanEst=mean(Est_Surv, na.rm=TRUE), 
            meanHyp = mean(`hypocotyl. length.cm`, na.rm=TRUE),
            meanHeight = mean(height.cm, na.rm=TRUE), 
            meanLength = mean(long.leaf.cm, na.rm=TRUE))
est_summary
#F1s had the highest establishment success, parents the lowest 
#parents had largest hypocotyl lengths and F2s had the lowest
#parents were tallest, F2s the shortest
#F2s had longest leaves, parents had the shortest 
```

## Pop Averages

```{r}
est_summary_pops <- establishment %>% 
  group_by(Pop.Type, pop) %>% 
  summarise(meanEst=mean(Est_Surv, na.rm=TRUE), 
            meanHyp = mean(`hypocotyl. length.cm`, na.rm=TRUE),
            meanHeight = mean(height.cm, na.rm=TRUE), 
            meanLength = mean(long.leaf.cm, na.rm=TRUE))

est_summary_pops %>% 
  ggplot(aes(x=meanHyp, y=meanEst)) +
  geom_point() 
est_summary_pops %>% 
  ggplot(aes(x=meanHyp, y=meanEst)) +
  geom_point() + 
  facet_wrap(~Pop.Type)

est_summary_pops %>% 
  ggplot(aes(x=meanHeight, y=meanEst)) +
  geom_point() 
est_summary_pops %>% 
  ggplot(aes(x=meanHeight, y=meanEst)) +
  geom_point() + 
  facet_wrap(~Pop.Type)

est_summary_pops %>% 
  ggplot(aes(x=meanLength, y=meanEst)) +
  geom_point() 
est_summary_pops %>% 
  ggplot(aes(x=meanLength, y=meanEst)) +
  geom_point() + 
  facet_wrap(~Pop.Type)
```

## Quick Models

```{r}
hyp_for_models <- establishment %>% filter(!is.na(`hypocotyl. length.cm`))

hyp_est_model1 <- glm(Est_Surv ~ `hypocotyl. length.cm`, family=binomial, data=hyp_for_models)
summary(hyp_est_model1)

hyp_est_model2 <- glmer(Est_Surv ~ `hypocotyl. length.cm` + (1|Pop.Type), family=binomial, data=hyp_for_models)
summary(hyp_est_model2) #no significant relationship with hypocotyl length 
```

```{r}
height_for_models <- establishment %>% filter(!is.na(height.cm))

height_est_model1 <- glm(Est_Surv ~ height.cm, family=binomial, data=height_for_models)
summary(height_est_model1)

height_est_model2 <- glmer(Est_Surv ~ height.cm + (1|Pop.Type), family=binomial, data=height_for_models)
summary(height_est_model2) #sig pos relationship with height (taller survived better)
```

```{r}
length_for_models <- establishment %>% filter(!is.na(long.leaf.cm))

length_est_model1 <- glm(Est_Surv ~ long.leaf.cm, family=binomial, data=length_for_models)
summary(length_est_model1)

length_est_model2 <- glmer(Est_Surv ~ long.leaf.cm + (1|Pop.Type), family=binomial, data=length_for_models)
summary(length_est_model2) #sig pos relationship with height (longer survived better)
```

## Models by Pop type 

### Parents 
```{r}
parents_est <- establishment %>% 
  filter(Pop.Type=="Parent") %>% 
  filter(!is.na(height.cm)) %>% 
  filter(!is.na(long.leaf.cm))
unique(parents_est$pop)

height_est_model3 <- glmer(Est_Surv ~ height.cm + (1|pop), family=binomial, data=parents_est)
summary(height_est_model3)

length_est_model3 <- glmer(Est_Surv ~ long.leaf.cm + (1|pop), family=binomial, data=parents_est)
summary(length_est_model3)

##predictions for figures:
parents_est_preds <- tibble(height.cm=seq(from = 0.3, to=30, length.out=280),
                            long.leaf.cm=seq(from = 0.2, to=8, length.out=280))

height_est_preds <- tibble(predictions=predict(height_est_model3, 
                                               newdata=parents_est_preds,
                                           re.form= NA, type="response")) %>% 
  bind_cols(parents_est_preds) 
height_est_preds %>% ggplot(aes(height.cm, predictions)) +
  geom_point() +
  labs(x="Height 3 Weeks Post-Strat", y="Predicted Establishment", title="Parents")

length_est_preds <- tibble(predictions=predict(length_est_model3, 
                                               newdata=parents_est_preds,
                                           re.form= NA, type="response")) %>% 
  bind_cols(parents_est_preds) 
length_est_preds %>% ggplot(aes(long.leaf.cm, predictions)) +
  geom_point() +
  labs(x="Leaf Length 3 Weeks Post-Strat", y="Predicted Establishment", title="Parents")
```

```{r}
height_est_preds %>% filter(predictions>.50) %>% summarise(min(height.cm))
#Min height for prediction of greater than 50% establishment = 3.92
parents_est %>% mutate(BigEnough=if_else(height.cm>=3.92, 1, 0)) %>% 
  group_by(BigEnough) %>% 
  summarise(n=n())
#33% of plants were "Big Enough"

length_est_preds %>% filter(predictions>.50) %>% summarise(min(long.leaf.cm))
#Min height for prediction of greater than 50% establishment = 2.27
parents_est %>% mutate(BigEnough=if_else(long.leaf.cm>=2.27, 1, 0)) %>% 
  group_by(BigEnough) %>% 
  summarise(n=n())
#12% of plants were "Big Enough"
```


### Crosses 
```{r}
crosses_est <- establishment %>% 
  filter(Pop.Type!="Parent") %>% 
  filter(!is.na(height.cm)) %>% 
  filter(!is.na(long.leaf.cm))
unique(crosses_est$pop) #74 cross types 

height_est_model4 <- glmer(Est_Surv ~ height.cm + (1|pop), family=binomial, data=crosses_est)
summary(height_est_model4) #height not sig

length_est_model4 <- glmer(Est_Surv ~ long.leaf.cm + (1|pop), family=binomial, data=crosses_est)
summary(length_est_model4)

##predictions for figures:
crosses_est_preds <- tibble(long.leaf.cm=seq(from = 0.1, to=26, length.out=541))

length_est_preds <- tibble(predictions=predict(length_est_model4, 
                                               newdata=crosses_est_preds,
                                           re.form= NA, type="response")) %>% 
  bind_cols(crosses_est_preds) 
length_est_preds %>% ggplot(aes(long.leaf.cm, predictions)) +
  geom_point() +
  labs(x="Leaf Length 3 Weeks Post-Strat", y="Predicted Establishment", title="Crosses")
```

```{r}
length_est_preds %>% filter(predictions>.50) %>% summarise(min(long.leaf.cm))
#Min height for prediction of greater than 50% establishment = 1.73
crosses_est %>% mutate(BigEnough=if_else(long.leaf.cm>=1.73, 1, 0)) %>% 
  group_by(BigEnough) %>% 
  summarise(n=n())
#47.5% of plants were "Big Enough"
```