---
title: "WL2_2025_TotalFitness"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Total Fitness for plants planted in 2025

Takes into account 2025 and 2026 data

## Libraries

```{r}
library(tidyverse)

sem <- function(x, na.rm=FALSE) {  #for calculating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 
```

## Read in data

```{r}
wintsurv_2025_2026 <- read_csv("../input/WL2_2026_Data/CorrectedCSVs/WL2_2026_WinterSurv_corrected.csv")
unique(wintsurv_2025_2026$death.date) #contains all year 1 info too

surv_2026 <- read_csv("../input/WL2_2026_Data/CorrectedCSVs/WL2_mort_pheno_20260820_corrected.csv") %>% 
  select(-survey.notes)#for surv to budding - need to update this with end of season data
unique(surv_2026$bud.date)

fruits_2026 <- read_csv("../input/WL2_2026_Data/CorrectedCSVs/WL2_ann_cens_20260820_corrected.csv") %>% 
  select(-survey.notes) #for fruit number - need to update this with end of season data
```

## Pop Info

```{r}
pop_info_2025 <- read_csv("../input/WL2_2025_Data/2025_Pop_Loc_Info Updated.csv") %>% 
  select(status:Unique.ID) %>% 
  mutate(Pop.Type=if_else(str_detect(pop.id, "\\) x"), "F2",
                          if_else(str_detect(pop.id, "x"), "F1",
                          if_else(pop.id=="buffer" | is.na(pop.id), NA,
                                  "Parent"
                          )))) #define different pop types 
pop_info_2026 <- read_csv("../input/WL2_2026_Data/Buffer New Bed Map_Corrected.csv") %>%
  rename(rep=Rep, Pop.Type=Type) 
```

## Elevation Info / Climate distance

```{r}
clim_dist_2025 <- read_csv("../output/Climate/WL2_2025_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
head(clim_dist_2025)

clim_dist_2025_wide <- clim_dist_2025 %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop.id=parent.pop)
```

## Calculate y1 fitness and remove plants not planted in 2025

```{r}
wintsurv_2025_2026 %>%  
  left_join(pop_info_2025) %>% 
  filter(status=="available") %>% filter(!is.na(bud.date)) #some plants flowering at wint surv check 

y1_fitness <- wintsurv_2025_2026 %>% 
  select(bed:Unique.ID, bud.date, death.date, survey.notes) %>% 
  left_join(pop_info_2025) %>% 
  filter(Unique.ID != "buffer") %>% #remove buffers
  filter(status=="available") %>%  #keep only plants planted in 2025
  select(block, bed:Unique.ID, Pop.Type, pop.id:rep, bud.date:death.date) %>% 
  filter(Unique.ID!="2605", Unique.ID!="1950",
         Unique.ID!="1675") %>% #remove plants that were dead at planting 
  mutate(death.date=mdy(death.date)) %>% #convert to date format 
  mutate(Establishment = if_else(is.na(death.date), 1, 
                                 if_else(death.date < "2025-06-21", 0, 1)), #establishment = first 3 weeks post-transplant 
         Y1Surv = if_else(Establishment==0, NA, #can't survive year 1 if you didn't establish 
                          if_else(is.na(death.date), 1, 
                                        if_else(death.date < "2025-11-01", 0, 1))), #year 1 ended in Oct
         WintSurv = if_else(Establishment==0 | Y1Surv==0, NA, #can only have wint surv if survived y1 
                            if_else(is.na(death.date), 1, 0))) 

y1_fitness %>% filter(WintSurv==1) #126 plants survived the winter 
```

## Calculate y2 fitness and remove plants not planted in 2025

```{r}
surv_2026 %>% left_join(pop_info_2026) %>% filter(status=="2025-survivor") %>% filter(is.na(death.date)) %>% filter(is.na(bud.date)) #1 2025 plant alive that has not reproduced yet 

y2_fitness <- pop_info_2026 %>% 
  left_join(surv_2026) %>% 
  left_join(fruits_2026) %>% 
  filter(Unique.ID!="buffer", !is.na(Unique.ID)) %>% 
  filter(status=="2025-survivor") %>% 
  mutate(SurvtoBud=if_else(Unique.ID=="2640", 1, #missed the bud date for this plant but it did reproduce 
                           if_else(!is.na(bud.date), 1, 0))) %>% 
  select(Unique.ID, pop.id, mf, rep, SurvtoBud, num.fruit)

y2_fitness %>% filter(pop.id=="BH")
#2615 and 1600 were reproductive in July data, investigate what happened 
```

## Merge y1 and y2 fitness ---\> total fitnes

```{r}
total_fit_2025plants <- y1_fitness %>% 
  select(-bud.date, -death.date) %>% 
  #mutate(mf=as.character(mf)) %>% #needed for the merge
  left_join(y2_fitness) %>% 
  mutate(ProbFruit=if_else(is.na(num.fruit) | num.fruit==0, 0, 1),
         TotalFitness=if_else(ProbFruit==0, 0, num.fruit))
  
head(total_fit_2025plants)
summary(total_fit_2025plants)
write_csv(total_fit_2025plants, "../output/WL2_Traits/WL2_2025_AllFitness.csv")
```

## Means

```{r}
total_fit_2025plants_summary <- total_fit_2025plants %>% 
  group_by(Pop.Type, pop.id) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruit=mean(num.fruit, na.rm=TRUE), semFruit=sem(num.fruit, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE))

total_fit_2025plants_summary
```

## Quick Figures

### Establishment
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanEst), y=meanEst, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Establishment", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanEst, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Establishment", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanEst), y=meanEst)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Establishment")
```

### Y1 Surv
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanY1Surv), y=meanY1Surv, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Y1 Surv", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanY1Surv, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Y1 Surv", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanY1Surv), y=meanY1Surv)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Y1 Surv")
```

### Winter Surv

```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  mutate(meanWintSurv=if_else(meanWintSurv=="NaN", NA, meanWintSurv)) %>% 
  filter(!is.na(meanWintSurv)) %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanWintSurv), y=meanWintSurv, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Winter Survival", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  mutate(meanWintSurv=if_else(meanWintSurv=="NaN", NA, meanWintSurv)) %>% 
  filter(!is.na(meanWintSurv)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanWintSurv, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Winter Survival", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  mutate(meanWintSurv=if_else(meanWintSurv=="NaN", NA, meanWintSurv)) %>% 
  filter(!is.na(meanWintSurv)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanWintSurv), y=meanWintSurv)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Winter Survival")
```

### Surv to Budding 
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  mutate(meanSurvtoBud=if_else(meanSurvtoBud=="NaN", NA, meanSurvtoBud)) %>% 
  filter(!is.na(meanSurvtoBud)) %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanSurvtoBud), y=meanSurvtoBud, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Surv to Buddding", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  mutate(meanSurvtoBud=if_else(meanSurvtoBud=="NaN", NA, meanSurvtoBud)) %>% 
  filter(!is.na(meanSurvtoBud)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanSurvtoBud, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Surv to Buddding", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  mutate(meanSurvtoBud=if_else(meanSurvtoBud=="NaN", NA, meanSurvtoBud)) %>% 
  filter(!is.na(meanSurvtoBud)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanSurvtoBud), y=meanSurvtoBud)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Surv to Buddding")
```

### Fruit #
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  mutate(meanFruit=if_else(meanFruit=="NaN", NA, meanFruit)) %>% 
  filter(!is.na(meanFruit)) %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanFruit), y=meanFruit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanFruit-semFruit,
                    ymax=meanFruit+semFruit),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Fecundity", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  mutate(meanFruit=if_else(meanFruit=="NaN", NA, meanFruit)) %>% 
  filter(!is.na(meanFruit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanFruit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanFruit-semFruit,
                    ymax=meanFruit+semFruit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Fecundity", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  mutate(meanFruit=if_else(meanFruit=="NaN", NA, meanFruit)) %>% 
  filter(!is.na(meanFruit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanFruit), y=meanFruit)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanFruit-semFruit,
                    ymax=meanFruit+semFruit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Fecundity")
```

### Prob Fruit
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  mutate(meanProbProbFruit=if_else(meanProbFruit=="NaN", NA, meanProbFruit)) %>% 
  filter(!is.na(meanProbFruit)) %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanProbFruit), y=meanProbFruit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Prob Rep", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  mutate(meanProbFruit=if_else(meanProbFruit=="NaN", NA, meanProbFruit)) %>% 
  filter(!is.na(meanProbFruit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanProbFruit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Prob Rep", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  mutate(meanProbFruit=if_else(meanProbFruit=="NaN", NA, meanProbFruit)) %>% 
  filter(!is.na(meanProbFruit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanProbFruit), y=meanProbFruit)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Prob Rep")
```

### Total fruit 
```{r}
total_fit_2025plants_summary %>% 
  filter(Pop.Type=="Parent") %>% 
  mutate(meanTotalFit=if_else(meanTotalFit=="NaN", NA, meanTotalFit)) %>% 
  filter(!is.na(meanTotalFit)) %>% 
  left_join(clim_dist_2025_wide) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanTotalFit), y=meanTotalFit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit),width=.2, 
                position =position_dodge(0.75)) +
  labs(x="Population", y="Avg Total Fitness", fill="Elevation (m)") +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme_classic()

total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F1") %>% 
  mutate(Donor.Pop=str_remove_all(pop.id, "WL2")) %>% 
  mutate(Donor.Pop=str_remove_all(Donor.Pop, " x ")) %>% 
  left_join(clim_dist_2025_wide, by=join_by(Donor.Pop==pop.id)) %>% 
  mutate(meanTotalFit=if_else(meanTotalFit=="NaN", NA, meanTotalFit)) %>% 
  filter(!is.na(meanTotalFit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, elev_m), y=meanTotalFit, fill=elev_m)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F1", y="Avg Total Fitness", fill="Donor Elevation (m)")


total_fit_2025plants_summary %>% 
  filter(Pop.Type=="F2") %>% 
  mutate(meanTotalFit=if_else(meanTotalFit=="NaN", NA, meanTotalFit)) %>% 
  filter(!is.na(meanTotalFit)) %>% 
  ggplot(aes(x=fct_reorder(pop.id, meanTotalFit), y=meanTotalFit)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit),
                width=.2, position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(x="F2", y="Avg Total Fitness")
```