---
title: "WL2_ProblemCheck"
author: "Brandie Quarles"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code for checking for problems in data 

## Annual Census
```{r}
#load the libraries
library(tidyverse)

#data <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_Annual_Census_20241023_corrected.csv")
data <- read_csv("../input/WL2_2025_Data/CorrectedCSVs/WL2_ann_cens_20251006_corrected.csv")
  #remove spaces in column names
  names(data) <- gsub(" ", "", colnames(data))
  
  #check for spaces in numbers
  data2 <- data %>% filter(grepl(" ", diam.mm) | grepl(" ", num.flw) | grepl(" ", num.fruit) | 
                             grepl(" ", long.fruit.cm) #| grepl(" ", total.branch) | 
                             #grepl(" ", overhd.diam) | grepl(" ", overhd.perp)
                           ) %>%
    mutate(problem="spaces")
  
  #check for extreme values
  data3 <- data
  data3 <- data3 %>% filter(diam.mm > 50, long.fruit.cm > 15) %>% mutate(problem="extreme value")
  
  #check for letters in number columns 
  data4 <- data %>% rowwise() %>% filter(!is.na(diam.mm)) %>% filter(is.na(as.numeric(diam.mm))) %>%
    mutate(problem="character")
  data6 <- data %>% rowwise() %>% filter(!is.na(total.branch)) %>% filter(is.na(as.numeric(total.branch))) %>%
    mutate(problem="character")
  data8 <- data %>% rowwise() %>% filter(!is.na(num.flw)) %>% filter(is.na(as.numeric(num.flw))) %>%
    mutate(problem="character")
  data9 <- data %>% rowwise() %>% filter(!is.na(num.fruit)) %>% filter(is.na(as.numeric(num.fruit))) %>%
    mutate(problem="character")
  data10 <- data %>% rowwise() %>% filter(!is.na(long.fruit.cm)) %>% filter(is.na(as.numeric(long.fruit.cm))) %>%
    mutate(problem="character")
 # data11 <- data %>% rowwise() %>% filter(!is.na(overhd.diam)) %>% filter(is.na(as.numeric(overhd.diam))) %>%
 #   mutate(problem="character")
 # data12 <- data %>% rowwise() %>% filter(!is.na(overhd.perp)) %>% filter(is.na(as.numeric(overhd.perp))) %>%
 #   mutate(problem="character")
  
  #combine into one problems list
  data_probs <- rbind(data2, data3, data4, data6, data8, data9, data10 #, 
                      #data11, data12 #no diameter in anncens data 2025
                      )
  data_probs
  write_csv(data_probs, "../output/WL2_Traits/anncens_probs.csv")
```

## Mortality
```{r}
#load the libraries
library(tidyverse)
#tutorial at https://bookdown.org/ansellbr/WEHI_tidyR_course_book/week-4-part-3.html
#data_files <- list.files('../input/WL2_2024_Data/CorrectedCSVs/',pattern='mort.*corrected.*csv',ignore.case=TRUE)  #edit this to be correct path 
data_files <- list.files('../input/WL2_2025_Data/CorrectedCSVs/',pattern='mort.*corrected.*csv',ignore.case=TRUE)  #edit this to be correct path 
data_files #make this specific to mortality or size

data_names <- str_remove(data_files, pattern = ".csv")
data_names

for (i in data_names) {
  #set up variable file names
 # in_file <- paste("../input/WL2_2024_Data/CorrectedCSVs/", i, '.csv', sep = "")   #edit this to be correct path 
  in_file <- paste("../input/WL2_2025_Data/CorrectedCSVs/", i, '.csv', sep = "")   #edit this to be correct path 
  out_table <- paste("../output/WL2_Traits/", i, '_dataprobs.csv', sep="")
  
  #data checking code
  data <- read_csv(in_file)
  
  #remove spaces in column names
  names(data) <- gsub(" ", "", colnames(data))
  
  #check for spaces in numbers
  data2 <- data %>% filter(grepl(" ", bud.date) | grepl(" ", flower.date) | grepl(" ", fruit.date) | grepl(" ", last.FL.date) | grepl(" ", last.FR.date) | grepl(" ", death.date)) %>% mutate(problem="spaces")
  
  #check for non-date format
  data5 <- data %>% rowwise() %>% filter(!is.na(bud.date)) %>% 
    filter(is.na(mdy(bud.date))) %>% 
    mutate(problem="non-date")
  
  data6 <- data %>% rowwise() %>% filter(!is.na(flower.date)) %>% 
    filter(is.na(mdy(flower.date))) %>% 
    mutate(problem="non-date")
  
  data7 <- data %>% rowwise() %>% filter(!is.na(fruit.date)) %>% 
    filter(is.na(mdy(fruit.date))) %>% 
    mutate(problem="non-date")
  
  data8 <- data %>% rowwise() %>% filter(!is.na(last.FL.date)) %>% 
    filter(is.na(mdy(last.FL.date))) %>% 
    mutate(problem="non-date")
  
  data9 <- data %>% rowwise() %>% filter(!is.na(last.FR.date)) %>% 
    filter(is.na(mdy(last.FR.date))) %>% 
    mutate(problem="non-date")
  
  data10 <- data %>% rowwise() %>% filter(!is.na(death.date)) %>% 
    filter(is.na(mdy(death.date))) %>% 
    mutate(problem="non-date")
  
  #combine into one problems list
  data_probs <- bind_rows(data2, data5, data6, data7, data8, data9, data10)
  print(nrow(data_probs))
  write_csv(data_probs, path=out_table)
}
```

## Size Data - basic check 
```{r}
#load the libraries
library(tidyverse)
#tutorial at https://bookdown.org/ansellbr/WEHI_tidyR_course_book/week-4-part-3.html
data_files <- list.files('../input/WL2_2025_Data/CorrectedCSVs/',pattern='WL2_size.*corrected.*csv',ignore.case=TRUE)  #edit this to be correct path 
data_files #make this specific to mortality or size

data_names <- str_remove(data_files, pattern = ".csv")
data_names

for (i in data_names) {
  #set up variable file names
  in_file <- paste("../input/WL2_2025_Data/CorrectedCSVs/", i, '.csv', sep = "")   #edit this to be correct path 
  out_table <- paste("../output/WL2_Traits/", i, '_dataprobs.csv', sep="")
  
  #data checking code
  data <- read_csv(in_file)
  
  #remove spaces in column names
  names(data) <- gsub(" ", "", colnames(data))
  
  #check for spaces in numbers
  data2 <- data %>% filter(grepl(" ", height.cm)) %>% 
    mutate(problem="spaces", height.cm=as.character(height.cm))
  
  #check for extreme values
  data3 <- data %>% mutate(height.cm=as.double(height.cm))
  data3 <- data3 %>% filter(height.cm>30) %>% 
    mutate(problem="extreme value", height.cm=as.character(height.cm))
  
  #check for letters in number columns 
  data4 <- data %>% rowwise() %>% filter(!is.na(herbv.scale) & herbv.scale !="-" & herbv.scale != "N/A") %>% 
    filter(is.na(as.numeric(herbv.scale))) %>% 
    mutate(problem="character", herbv.scale=as.character(herbv.scale))
  
  data5 <- data %>% rowwise() %>% filter(!is.na(height.cm) & height.cm !="-" & height.cm != "N/A") %>% 
    filter(is.na(as.numeric(height.cm))) %>% 
    mutate(problem="character", height.cm=as.character(height.cm))
  
  data6 <- data %>% rowwise() %>% filter(!is.na(overhd.diam) & overhd.diam !="-" & overhd.diam != "N/A") %>% 
    filter(is.na(as.numeric(overhd.diam))) %>% 
    mutate(problem="character", overhd.diam=as.character(overhd.diam))
  
  data7 <- data %>% rowwise() %>% filter(!is.na(overhd.perp) & overhd.perp !="-" & overhd.perp != "N/A") %>% 
    filter(is.na(as.numeric(overhd.perp))) %>% 
    mutate(problem="character", overhd.perp=as.character(overhd.perp))
  
  #combine into one problems list
  data_probs <- rbind(data2, data3, data4, data5, data6, data7)
  print(nrow(data_probs))
  write_csv(data_probs, path=out_table)
}
```


## Size Data (temporal check)
Check for data when there is no data in previous week 
* Reason: found a case where someone wrote the data in the wrong row (in the row of a dead plant) 

--*COME BACK TO THIS WHEN FIX ABOVE ISSUES 

```{r}
library(tidyverse)

files <- dir("../input/WL2_2025_Data/CorrectedCSVs/",
             pattern="WL2_size",
             full.names=TRUE)
files #list of files 

dat <- tibble(path=files, filename=basename(path)) #storing data in tibble
dat

# create a new column, "date"
dat2 <- dat %>%
  mutate(survey_date=str_extract(filename, "_2[0-9]*"), 
         survey_date=str_remove(survey_date, "_"), 
         survey_date=lubridate::ymd(survey_date))
dat2
```

### read in the files 
```{r}
dat3 <- dat2 %>% 
  mutate(sheets=map(path, 
                    read_csv, 
                    col_types=cols(.default=col_character()), # forces all columns to be character
    # this is needed because of data sheet problems that cause some numerics to be imported as character  
                    na = c("", "NA", "-", "N/A") # sets NA strings.
                    )) %>%
  select(-path)

dat3$sheets[[1]] # extract the first imported sheet to check that the above worked

map(dat3$sheets, colnames) %>% #check column names before merging 
  unlist() %>%
  unique() %>%
  sort()
```

### Unnest 
```{r}
#unnest
dat4 <- dat3 %>% unnest(sheets) %>% 
  select(filename:survey.notes, leaf.number)
head(dat4)
names(dat4)
#dat4 %>% filter(!is.na(pop)) #only in the csvs where 2023 plants had to be corrected 
```

### check for data issues
```{r}
dat4 %>% rowwise() %>% filter(!is.na(row)) %>% filter(is.na(as.numeric(row))) #no issues 
dat4 %>% rowwise() %>% filter(!is.na(height.cm)) %>% filter(is.na(as.numeric(height.cm))) #none
dat4 %>% rowwise() %>% filter(!is.na(leaf.number)) %>% filter(is.na(as.numeric(leaf.number))) #none 
dat4 %>% rowwise() %>% filter(!is.na(overhd.diam)) %>% filter(is.na(as.numeric(overhd.diam))) #none
dat4 %>% rowwise() %>% filter(!is.na(overhd.perp)) %>% filter(is.na(as.numeric(overhd.perp)))  #none
dat4 %>% rowwise() %>% filter(!is.na(herbv.scale)) %>% filter(is.na(as.numeric(herbv.scale)))  #none
dat4 %>% rowwise() %>% filter(!is.na(Unique.ID), Unique.ID!="buffer") %>% filter(is.na(as.numeric(Unique.ID)))  #all Y07 from 2023

unique(dat4$bed) 
dat4 %>% filter(bed=="c") #6/27, 8/7, 8/14, 8/21, 9/11, 9/18
dat4 %>% filter(bed=="E.") #7/25, 8/7, 8/21, 9/29
dat4 %>% filter(bed=="LL") #8/1
dat4 %>% filter(bed=="S") #8/7

unique(dat4$row) #no issues 

unique(dat4$col) 
dat4 %>% filter(col=="c") #8/7, 8/14, 8/21, 8/28, 9/4, 9/11, 9/18, 9/29

##NEED TO fix all above issues in csvs
```

### lag lead function
```{r}
unique(dat4$survey_date)

dat5 <- dat4 %>% 
  filter(Unique.ID!="buffer") %>% #remove buffers 
  mutate(across(c(row, leaf.number, height.cm, overhd.diam, overhd.perp), as.numeric)) %>% 
  mutate(censusN=ifelse(survey_date=="2025-06-09", 1,
                        ifelse(survey_date=="2025-06-27", 2,
                        ifelse(survey_date=="2025-07-11", 3, 
                        ifelse(survey_date=="2025-07-18", 4, 
                        ifelse(survey_date=="2025-07-25", 5, 
                        ifelse(survey_date=="2025-08-01", 6,
                        ifelse(survey_date=="2025-08-07", 7, 
                        ifelse(survey_date=="2025-08-14", 8,
                        ifelse(survey_date=="2025-08-21", 10,
                        ifelse(survey_date=="2025-08-28", 11,
                        ifelse(survey_date=="2025-09-04", 12,
                        ifelse(survey_date=="2025-09-11", 13,
                        ifelse(survey_date=="2025-09-18", 14,
                        ifelse(survey_date=="2025-09-24", 15,
                        ifelse(survey_date=="2025-09-29", 16,
                               NA))))))))))))))))
dat5 %>% filter(is.na(censusN)) #none 
```

### Check for data when there is no data in previous week 
Need to adjust this to account for when we started measuring only half the blocks each week 
```{r}
dat6 <- dat5 %>%  #by bed, row, col
  group_by(bed, row, col) %>% 
  mutate(previous_census_height=lag(height.cm, order_by = censusN), 
         previous_census_leaves=lag(leaf.number, order_by = censusN),
         previous_census_overhd.diam=lag(overhd.diam, order_by = censusN), 
         previous_census_overhd.perp=lag(overhd.perp, order_by = censusN)) %>% 
  select(censusN, bed, row, col, previous_census_height, height.cm, 
         previous_census_leaves, leaf.number,
         previous_census_overhd.diam, overhd.diam,
         previous_census_overhd.perp, overhd.perp,
         survey.notes) %>% 
  arrange(bed, row, col, censusN)
dat8 <- dat6 %>% filter(censusN!=1) %>% filter(is.na(previous_census_height), !is.na(height.cm)) #621 rows 


dat7 <- dat5 %>% #by uniqueID
  group_by(unique.ID) %>% 
  mutate(previous_census_height=lag(height.cm, order_by = censusN), 
         previous_census_length=lag(long.leaf.cm, order_by = censusN),
         previous_census_overhd.diam=lag(overhd.diam, order_by = censusN), 
         previous_census_overhd.perp=lag(overhd.perp, order_by = censusN)) %>% 
  select(bed, row, col, survey_date,censusN,unique.ID, previous_census_height, height.cm, 
         previous_census_length, long.leaf.cm, 
         previous_census_overhd.diam, overhd.diam,
         previous_census_overhd.perp, overhd.perp,
         survey.notes) %>% 
  arrange(unique.ID, censusN)
head(dat7)
#Check for data when there is no data in previous week 
dat9 <- dat7 %>% filter(censusN!=1) %>% filter(is.na(previous_census_height), !is.na(height.cm)) #607 rows 
dat9
write.csv(dat9, "../output/WL2_Traits/WL2_MissingDataPrevWeek.csv", row.names = FALSE)
```

