---
title: "WL2_Single_Time_Surv"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Analysis of Survival at WL2 2024 Garden to Plant for BC2 crosses

To Do:
-   See Julin's code for poperly calculating sem for surv
-   Convert to yes/no for each parent pop

## Relevant Libraries and Functions
```{r}
library(tidyverse)
library(tidymodels)
tidymodels_prefer()
library(emmeans) #for post-hoc pairwise comparisons 
library(lmerTest) #for mixed effect models
conflicted::conflicts_prefer(lmerTest::lmer)
library(broom.mixed) #tidy method for lmerTest
library(emmeans) #for post-hoc pairwise comparisons 
library(naniar) #replaces values with NA
library(brms)

sem <- function(x, na.rm=FALSE) {           #for caclulating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 

elev_three_palette <- c("#0043F0", "#C9727F", "#F5A540") #colors from Gremer et al 2019
elev_order <- c("High", "Mid", "Low") #for proper arrangement in figures 
```

## Load pop and location data
```{r}
plant_info <- read_csv("../input/WL2_2024_Data/WL2_Final_2023_2024_Pop_Loc_Info.csv")
head(plant_info)
unique(plant_info$Pop.Type) #info about whether the plant is from 2023, an F1, F2, or parent 
unique(plant_info$status) #status info for planting (i.e. available spot to plant or not)
plant_info_to_merge <- plant_info %>% 
  select(Pop.Type, block, parent.pop=pop,mf:unique.ID) %>% 
  filter(!is.na(parent.pop))

pop_loc <- read_csv("../input/Strep_tort_locs.csv")
head(pop_loc)

unique(pop_loc$`Site code`)
unique(plant_info_to_merge$parent.pop)
#need to change YOSE to YO
pop_loc_yo <- pop_loc %>% mutate(parent.pop = str_replace(`Site code`, "YOSE(\\d+)", "YO\\1")) %>% select(Lat, Long, elev_m=`Elevation (m)`, parent.pop)
unique(pop_loc_yo$parent.pop)

pop_elev <- left_join(plant_info_to_merge, pop_loc_yo)
head(pop_elev)
```

## Load the mort/pheno data
```{r}
mort_pheno_1023 <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_mort_pheno_20241023_corrected.csv", 
                            na = c("", "NA", "-", "N/A")) %>% arrange(death.date)
head(mort_pheno_1023)
names(mort_pheno_1023)
unique(mort_pheno_1023$bed) #D and "D."
unique(mort_pheno_1023$death.date)  
#some dates should be checked: 6/24, 6/27 - both were data verifcation errors, corrected on csv. 

mort_pheno_1023_nobuff <- mort_pheno_1023 %>% 
  filter(unique.ID !="buffer") %>% 
  filter(!is.na(unique.ID))
```

## Merge with location info 
```{r}
oct_mort_loc <- left_join(mort_pheno_1023_nobuff, pop_elev) 
head(oct_mort_loc)
names(oct_mort_loc)

oct_mort_loc %>% filter(!is.na(missing.date)) #11 2024 plants with a missing date & 1 2023 plant that went missing 
oct_mort_loc %>% filter(Pop.Type=="2023-survivor") # double checked none of these plants were actually alive (no data)
```

## Survival 

### Add Surv columns 
```{r}
wl2_surv <- oct_mort_loc %>% 
  filter(Pop.Type != "2023-TM2-fruit") %>% #take out 2023 fruiting locations 
  filter(is.na(missing.date)) %>% #take out plants that went missing 
  mutate(Surv_to_Oct = if_else(is.na(death.date), 1, 0), #surv to end of 2024 survey season
         Surv_Post_Transplant = if_else(is.na(death.date), 1,
           if_else(death.date=="6/18/24" | death.date=="6/25/24", 0, 1))) %>% #surv 2 weeks post-transplant
  select(Lat:elev_m, Pop.Type:rep, block:unique.ID, death.date, Surv_to_Oct, Surv_Post_Transplant, missing.date, survey.notes)

head(wl2_surv)
tail(wl2_surv)
```

```{r}
xtabs(~Surv_to_Oct+Pop.Type, data=wl2_surv) #numbers look right 
#(830 2024 plants - 11 went missing in the field) - 14% overall survival 
#(131 2023 plants - 1 went missing in the field) - 19% overall survival 

xtabs(~Surv_Post_Transplant+Pop.Type, data=wl2_surv)
#(830 2024 plants - 3 went missing in the field) - 77% overall survival 
```

## Quick Look at 2024 Parent Pops
```{r}
meansurv_2024_parents <- wl2_surv %>% 
  filter(Pop.Type=="Parent") %>% 
  group_by(parent.pop, elev_m) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_2024_parents #variable planting sample sizes (some as small as 2)

meansurv_2024_parents %>% 
  ggplot(aes(x=fct_reorder(parent.pop, mean_Surv_to_Oct), y=mean_Surv_to_Oct, fill=elev_m)) + 
  geom_col(width = 0.7,position = position_dodge(0.75), colour="black") +
  labs(x="Parent Population", y="Survival to Oct 2024", fill="Elevation (m)") +
  theme_classic() + 
  ylim(0,1) +
  #scale_y_continuous(expand = c(0, 0)) +
  geom_text(data = meansurv_2024_parents, aes(label = N_Surv), vjust = -1) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=25))
ggsave("../output/WL2_Traits/2024ParentSurvtoOct.png", width = 12, height = 6, units = "in")

meansurv_2024_parents %>% 
  ggplot(aes(x=fct_reorder(parent.pop, mean_Surv_Post_Transplant), y=mean_Surv_Post_Transplant, fill=elev_m)) + 
  geom_col(width = 0.7,position = position_dodge(0.75), colour="black") +
  labs(x="Parent Population", y="Survival Two Weeks \n  Post-Transplant", fill="Elevation (m)") +
  theme_classic() + 
  coord_cartesian(ylim = c(0, 1.25)) +
  scale_y_continuous(breaks = c(0.00, 0.25, 0.50, 0.75, 1.00, 1.25)) +
  #scale_y_continuous(expand = c(0, 0)) +
  geom_text(data = meansurv_2024_parents, aes(label = N_Surv), vjust = -1) +
  scale_fill_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=25))
ggsave("../output/WL2_Traits/2024ParentSurvPostTransplant.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_surv_parents <- wl2_surv %>% 
  filter(Pop.Type=="Parent")

lmesurv1 <- glmer(Surv_to_Oct ~ 1 + (1|parent.pop), 
                  data = wl2_surv_parents, 
                  family = binomial(link = "logit"),
                  nAGQ=0, #uses the adaptive Gaussian quadrature instead the Laplace approximation. Ask Julin about this 
                  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lmesurv1)

#to test for significance of random effect: 
#the most common way to do this is to use a likelihood ratio test, i.e. fit the full and reduced models (the reduced model is the model with the focal variance(s) set to zero). 
m00 <- glm(Surv_to_Oct~ 1, wl2_surv_parents, family = binomial("logit"))
anova(lmesurv1,m00) #model with random effects has a higher likelihood 

lmesurv2 <- glm(Surv_to_Oct ~ 0 + parent.pop, family = binomial, data=wl2_surv_parents)
summary(lmesurv2)
anova(lmesurv2)

coef(lmesurv2) %>% inv_logit_scaled()
summary(lmesurv2)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

EMM <- emmeans(lmesurv2, "parent.pop")
EMM  
contrast(EMM, "pairwise") #BH is different from TM2 and WL2
```

```{r}
lmesurv3 <- glmer(Surv_Post_Transplant ~ 1 + (1|parent.pop), 
                  data = wl2_surv_parents, 
                  family = binomial(link = "logit"),
                  nAGQ=0, #uses the adaptive Gaussian quadrature instead the Laplace approximation. Ask Julin about this 
                  control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

summary(lmesurv3)

#to test for significance of random effect: 
#the most common way to do this is to use a likelihood ratio test, i.e. fit the full and reduced models (the reduced model is the model with the focal variance(s) set to zero). 
m00 <- glm(Surv_Post_Transplant~ 1, wl2_surv_parents, family = binomial("logit"))
anova(lmesurv3,m00) #model with random effects has a higher likelihood 


lmesurv4 <- glm(Surv_Post_Transplant ~ 0 + parent.pop, family = binomial, data=wl2_surv_parents)
summary(lmesurv4)
anova(lmesurv4)

coef(lmesurv4) %>% inv_logit_scaled()
summary(lmesurv4)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

EMM <- emmeans(lmesurv4, "parent.pop")
EMM  
contrast(EMM, "pairwise") #BH is different from TM2 and WL2
```


## F1s

```{r}
wl2_surv_F1 <- wl2_surv %>% 
  filter(Pop.Type=="F1") %>% 
  unite(Field_Loc, bed:col, sep="_") %>% 
  select(Pop.Type:parent.pop, Field_Loc, unique.ID:Surv_Post_Transplant, survey.notes) %>% 
  separate_wider_delim(parent.pop, " x ", names = c("maternal.pop", "paternal.pop"), cols_remove = FALSE) %>% 
  mutate(WL2.cross = if_else(maternal.pop=="WL2" | paternal.pop=="WL2", TRUE, FALSE))
wl2_surv_F1
xtabs(~Surv_to_Oct+WL2.cross, data=wl2_surv_F1) #slightly higher surv in WL2 crosses 
xtabs(~Surv_Post_Transplant+WL2.cross, data=wl2_surv_F1) #slightly higher surv in TM2 crosses
```

Filter to only F1s with WL2 involved 
```{r}
wl2_surv_wl2F1s <- wl2_surv_F1 %>% filter(WL2.cross=="TRUE")  
unique(wl2_surv_wl2F1s$parent.pop) #only 7 F1s with WL2 involved
xtabs(~Surv_to_Oct+maternal.pop, data=wl2_surv_wl2F1s) 
xtabs(~Surv_Post_Transplant+maternal.pop, data=wl2_surv_wl2F1s) 
xtabs(~Surv_to_Oct+paternal.pop, data=wl2_surv_wl2F1s) 
xtabs(~Surv_Post_Transplant+paternal.pop, data=wl2_surv_wl2F1s) 
#sample sizes so low, it's hard to feel confident in any trends 
```

### Calculate proportions of each plant for analysis 
```{r}
wl2_surv_F1_props <- wl2_surv_F1 %>% 
  filter(WL2.cross=="TRUE") %>% #if want TM2 F1s just # this out 
  mutate(prop.WL2=str_count(parent.pop, "WL2")/2,
         prop.CC=str_count(parent.pop, "CC")/2,
         prop.BH=str_count(parent.pop, "BH")/2,
         prop.WV=str_count(parent.pop, "WV")/2,
         prop.LV1=str_count(parent.pop, "LV1")/2,
         prop.TM2=str_count(parent.pop, "TM2")/2,
         prop.SQ3=str_count(parent.pop, "SQ3")/2,
         prop.DPR=str_count(parent.pop, "DPR")/2,
         prop.YO11=str_count(parent.pop, "YO11")/2)

summary(wl2_surv_F1_props)

xtabs(~Surv_to_Oct+prop.BH, data=wl2_surv_F1_props)
xtabs(~Surv_to_Oct+prop.WV, data=wl2_surv_F1_props)
xtabs(~Surv_to_Oct+prop.LV1, data=wl2_surv_F1_props)
xtabs(~Surv_to_Oct+prop.TM2, data=wl2_surv_F1_props)
xtabs(~Surv_to_Oct+prop.SQ3, data=wl2_surv_F1_props)
xtabs(~Surv_to_Oct+prop.DPR, data=wl2_surv_F1_props)
```

```{r}
m1 <- glm(Surv_to_Oct ~ prop.BH+prop.WV+prop.LV1+prop.TM2+prop.SQ3+prop.DPR, family = binomial, data=wl2_surv_F1_props)

m2 <- glm(Surv_Post_Transplant ~ prop.BH+prop.WV+prop.LV1+prop.TM2+prop.SQ3+prop.DPR, family = binomial, data=wl2_surv_F1_props)

m3 <- glm(Surv_to_Oct ~ maternal.pop, family = binomial, data=wl2_surv_F1_props)

m4 <- glm(Surv_Post_Transplant ~ maternal.pop, family = binomial, data=wl2_surv_F1_props)
```

```{r}
summary(m1)
summary(m2)
summary(m3)
summary(m4)
```

Have to convert using inv_logit

coefficients
```{r}
results1 <- c(coef(m1)[1], #intercept
             coef(m1)[2:7] + coef(m1)[1]) %>% #coefficients + intercept
  inv_logit_scaled()

results1

results2 <- c(coef(m2)[1], #intercept
             coef(m2)[2:7] + coef(m2)[1]) %>% #coefficients + intercept
  inv_logit_scaled()

results2

results3 <- c(coef(m3)[1], #intercept
             coef(m3)[2:7] + coef(m3)[1]) %>% #coefficients + intercept
  inv_logit_scaled()

results3

results4 <- c(coef(m4)[1], #intercept
             coef(m4)[2:7] + coef(m4)[1]) %>% #coefficients + intercept
  inv_logit_scaled()

results4
```

error
```{r}
summary(m1)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

summary(m2)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

summary(m3)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

summary(m4)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()

#error is really high 
```

### Yes/No Parents
```{r}
wl2_surv_F1_binary <- wl2_surv_F1 %>% 
 # filter(WL2.cross=="TRUE") %>% #if want TM2 F1s just # this out 
  mutate(WL2=if_else(str_detect(parent.pop, "WL2"), 1, 0),
         CC=if_else(str_detect(parent.pop, "CC"), 1, 0),
         BH=if_else(str_detect(parent.pop, "BH"), 1, 0),
         WV=if_else(str_detect(parent.pop, "WV"), 1, 0),
         LV1=if_else(str_detect(parent.pop, "LV1"), 1, 0),
         TM2=if_else(str_detect(parent.pop, "TM2"), 1, 0),
         SQ3=if_else(str_detect(parent.pop, "SQ3"), 1, 0),
         DPR=if_else(str_detect(parent.pop, "DPR"), 1, 0),
         YO11=if_else(str_detect(parent.pop, "YO11"), 1, 0))
head(wl2_surv_F1_binary, 20)
summary(wl2_surv_F1_binary)
#switch to long format?
#could try switching to character?

xtabs(~Surv_to_Oct+WL2, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+CC, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+BH, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+WV, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+LV1, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+TM2, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+SQ3, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+DPR, data=wl2_surv_F1_binary)
xtabs(~Surv_to_Oct+YO11, data=wl2_surv_F1_binary)
```

```{r}
#try with random effects with glmmer - could try calculating 
surv_parent_binary_m1 = glm(Surv_to_Oct ~ 1 + (1|WL2)+(1|BH)+WV+LV1+TM2+SQ3+DPR, family = binomial, data=wl2_surv_F1_binary)
#try bernoulli instead of binomial 
summary(surv_parent_binary_m1)

results1 <- c(coef(surv_parent_binary_m1)[1], #intercept
             coef(surv_parent_binary_m1)[2:7] + coef(surv_parent_binary_m1)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results1 #what's the effect of each parent on survival compared to DPR

summary(surv_parent_binary_m1)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled() #code is working correctly, inv_logit really high numbers so it just returns 1 (hitting the upper limit) #Note: this only works b/c this is a binomial variable (and not a continuous one)
#if it was continuous, would be error around the slope 
#error really high?
```

```{r}
surv_parent_binary_m2 = glm(Surv_Post_Transplant ~ WL2+BH+WV+LV1+TM2+SQ3+DPR, family = binomial, data=wl2_surv_F1_binary)

summary(surv_parent_binary_m2)

results2 <- c(coef(surv_parent_binary_m2)[1], #intercept
             coef(surv_parent_binary_m2)[2:7] + coef(surv_parent_binary_m2)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results2

summary(surv_parent_binary_m2)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
#error really high?
```

## F2s

```{r}
wl2_surv_F2 <- wl2_surv %>% 
  filter(Pop.Type=="F2") %>% 
  unite(Field_Loc, bed:col, sep="_") %>% 
  mutate(WL2.cross = if_else(str_detect(parent.pop, "WL2"), TRUE, FALSE)) %>% 
  select(WL2.cross, Pop.Type:parent.pop, Field_Loc, unique.ID:Surv_Post_Transplant, survey.notes) %>% 
  separate_wider_delim(parent.pop, ") x (", names = c("maternal.pops", "paternal.pops"), cols_remove = FALSE) %>%
  mutate(maternal.pops=str_remove(maternal.pops, "\\("), paternal.pops=str_remove(paternal.pops, "\\)")) 
wl2_surv_F2
```

BC1s
```{r}
wl2_surv_bc1 <- wl2_surv_F2 %>% 
  filter(WL2.cross=="TRUE") %>% 
  filter(paternal.pops=="WL2"|maternal.pops=="WL2")
wl2_surv_bc1
xtabs(~Surv_to_Oct+maternal.pops, data=wl2_surv_bc1)
xtabs(~Surv_Post_Transplant+maternal.pops, data=wl2_surv_bc1)
xtabs(~Surv_to_Oct+paternal.pops, data=wl2_surv_bc1)
xtabs(~Surv_Post_Transplant+paternal.pops, data=wl2_surv_bc1)
```

### Calculate yes/no for each parent 
```{r}
wl2_surv_F2_binary <- wl2_surv_F2 %>% 
  filter(WL2.cross=="TRUE") %>% #if want TM2 F1s just # this out 
  mutate(WL2=if_else(str_detect(parent.pop, "WL2"), 1, 0),
         CC=if_else(str_detect(parent.pop, "CC"), 1, 0),
         BH=if_else(str_detect(parent.pop, "BH"), 1, 0),
         WV=if_else(str_detect(parent.pop, "WV"), 1, 0),
         LV1=if_else(str_detect(parent.pop, "LV1"), 1, 0),
         TM2=if_else(str_detect(parent.pop, "TM2"), 1, 0),
         SQ3=if_else(str_detect(parent.pop, "SQ3"), 1, 0),
         DPR=if_else(str_detect(parent.pop, "DPR"), 1, 0),
         YO11=if_else(str_detect(parent.pop, "YO11"), 1, 0),
         maternal.WL2=if_else(str_detect(maternal.pops, "WL2"), 1, 0),
         maternal.CC=if_else(str_detect(maternal.pops, "CC"), 1, 0),
         maternal.BH=if_else(str_detect(maternal.pops, "BH"), 1, 0),
         maternal.WV=if_else(str_detect(maternal.pops, "WV"), 1, 0),
         maternal.LV1=if_else(str_detect(maternal.pops, "LV1"), 1, 0),
         maternal.TM2=if_else(str_detect(maternal.pops, "TM2"), 1, 0),
         maternal.SQ3=if_else(str_detect(maternal.pops, "SQ3"), 1, 0),
         maternal.DPR=if_else(str_detect(maternal.pops, "DPR"), 1, 0),
         maternal.YO11=if_else(str_detect(maternal.pops, "YO11"), 1, 0))
head(wl2_surv_F2_binary, 20)
summary(wl2_surv_F2_binary)

xtabs(~Surv_to_Oct+WL2, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+CC, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+BH, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+WV, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+LV1, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+TM2, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+SQ3, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+DPR, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+YO11, data=wl2_surv_F2_binary)

xtabs(~Surv_to_Oct+WL2, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+CC, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+BH, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+WV, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+LV1, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+TM2, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+SQ3, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+DPR, data=wl2_surv_F2_binary)
xtabs(~Surv_to_Oct+YO11, data=wl2_surv_F2_binary)
```

#### Plots with binary
```{r}
wl2_surv_F2_binary %>% 
  group_by(CC, Surv_to_Oct) %>% 
  ggplot(aes(x=CC, fill=Surv_to_Oct)) +
  geom_bar(position = "dodge", alpha=0.9, width=0.5) +
  facet_wrap(~Surv_to_Oct)

wl2_surv_F2_binary %>% 
  group_by(CC, Surv_to_Oct) %>% 
  ggplot(aes(x=BH, fill=Surv_to_Oct)) +
  geom_bar(position = "dodge", alpha=0.9, width=0.5) +
  facet_wrap(~Surv_to_Oct)

wl2_surv_F2_binary %>% 
  group_by(CC, Surv_to_Oct) %>% 
  ggplot(aes(x=DPR, fill=Surv_to_Oct)) +
  geom_bar(position = "dodge", alpha=0.9, width=0.5) +
  facet_wrap(~Surv_to_Oct)
```

#### GLMs with binary
```{r}
surv_parent_binary_m3 = glm(Surv_to_Oct ~ CC+BH+WV+LV1+TM2+SQ3+DPR+YO11, family = binomial, data=wl2_surv_F2_binary)

summary(surv_parent_binary_m3)

resultsm3 <- c(coef(surv_parent_binary_m3)[1], #intercept
             coef(surv_parent_binary_m3)[2:7] + coef(surv_parent_binary_m3)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
resultsm3

summary(surv_parent_binary_m3)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
#error really high?
```

```{r}
surv_parent_binary_m4 = glm(Surv_Post_Transplant ~ CC+BH+WV+LV1+TM2+SQ3+DPR+YO11, family = binomial, data=wl2_surv_F2_binary)

summary(surv_parent_binary_m4)

resultsm4 <- c(coef(surv_parent_binary_m4)[1], #intercept
             coef(surv_parent_binary_m4)[2:7] + coef(surv_parent_binary_m4)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
resultsm4

summary(surv_parent_binary_m4)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
#error really high?
```

```{r}
surv_parent_binary_m5 = glm(Surv_to_Oct ~ maternal.WL2+maternal.CC+maternal.BH+maternal.WV+maternal.LV1+maternal.TM2+maternal.SQ3+maternal.DPR+maternal.YO11, family = binomial, data=wl2_surv_F2_binary)

summary(surv_parent_binary_m5)

resultsm5 <- c(coef(surv_parent_binary_m5)[1], #intercept
             coef(surv_parent_binary_m5)[2:7] + coef(surv_parent_binary_m5)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
resultsm5

summary(surv_parent_binary_m5)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
#error really high?
```

```{r}
surv_parent_binary_m6 = glm(Surv_Post_Transplant ~ maternal.WL2+maternal.CC+maternal.BH+maternal.WV+maternal.LV1+maternal.TM2+maternal.SQ3+maternal.DPR+maternal.YO11, 
                            family = binomial, data=wl2_surv_F2_binary)

summary(surv_parent_binary_m6)

resultsm6 <- c(coef(surv_parent_binary_m6)[1], #intercept
             coef(surv_parent_binary_m6)[2:7] + coef(surv_parent_binary_m6)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
resultsm6

summary(surv_parent_binary_m6)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
#error really high?
```

### Calculate proportions of each plant for analysis 
```{r}
wl2_surv_F2_props <- wl2_surv_F2 %>% 
  filter(WL2.cross=="TRUE") %>% #if want TM2 F2s just # this out 
  #FOR KEEPING TRACK OF MATERNAL AND PATERNAL POPS
  separate_wider_delim(maternal.pops, " x ", names = c("Parent1", "Parent2"), cols_remove = FALSE, too_few = "align_start") %>%
  separate_wider_delim(paternal.pops, " x ", names = c("Parent3", "Parent4"), cols_remove = FALSE, too_few = "align_start") %>%
  mutate(totalParents=rowSums(!is.na(select(., "Parent1", "Parent2", "Parent3", "Parent4")))) %>% 
  mutate(prop.WL2=str_count(parent.pop, "WL2")/totalParents,
        prop.CC=str_count(parent.pop, "CC")/totalParents,
        prop.BH=str_count(parent.pop, "BH")/totalParents,
        prop.WV=str_count(parent.pop, "WV")/totalParents,
        prop.LV1=str_count(parent.pop, "LV1")/totalParents,
        prop.TM2=str_count(parent.pop, "TM2")/totalParents,
        prop.SQ3=str_count(parent.pop, "SQ3")/totalParents,
        prop.DPR=str_count(parent.pop, "DPR")/totalParents,
        prop.YO11=str_count(parent.pop, "YO11")/totalParents)
  #mutate(WL2prop=if_else(Parent1=="WL2" & Parent2=="WL2" & Parent3=="WL2" & Parent4=="WL2", 1, ))
                         #is there an easier way to do this?)) 
wl2_surv_F2_props

summary(wl2_surv_F2_props)
xtabs(~Surv_to_Oct+prop.WL2, data=wl2_surv_F2_props)
```

### Plot with props
```{r}
meansurv_wl2prop <- wl2_surv_F2_props %>% 
  group_by(prop.WL2) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_wl2prop 

meansurv_wl2prop %>% 
  ggplot(aes(x=prop.WL2, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_CCprop <- wl2_surv_F2_props %>% 
  group_by(prop.CC) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_CCprop 

meansurv_CCprop %>% 
  ggplot(aes(x=prop.CC, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_BHprop <- wl2_surv_F2_props %>% 
  group_by(prop.BH) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_BHprop 

meansurv_BHprop %>% 
  ggplot(aes(x=prop.BH, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_WVprop <- wl2_surv_F2_props %>% 
  group_by(prop.WV) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_WVprop 

meansurv_WVprop %>% 
  ggplot(aes(x=prop.WV, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_LV1prop <- wl2_surv_F2_props %>% 
  group_by(prop.LV1) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_LV1prop 

meansurv_LV1prop %>% 
  ggplot(aes(x=prop.LV1, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 


meansurv_TM2prop <- wl2_surv_F2_props %>% 
  group_by(prop.TM2) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_TM2prop 

meansurv_TM2prop %>% 
  ggplot(aes(x=prop.TM2, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_SQ3prop <- wl2_surv_F2_props %>% 
  group_by(prop.SQ3) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_SQ3prop 

meansurv_SQ3prop %>% 
  ggplot(aes(x=prop.SQ3, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_DPRprop <- wl2_surv_F2_props %>% 
  group_by(prop.DPR) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_DPRprop 

meansurv_DPRprop %>% 
  ggplot(aes(x=prop.DPR, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 

meansurv_YO11prop <- wl2_surv_F2_props %>% 
  group_by(prop.YO11) %>% 
  summarise(N_Surv = sum(!is.na(Surv_to_Oct)), 
            mean_Surv_to_Oct = mean(Surv_to_Oct,na.rm=(TRUE)), 
            mean_Surv_Post_Transplant = mean(Surv_Post_Transplant,na.rm=(TRUE)))
meansurv_YO11prop 

meansurv_YO11prop %>% 
  ggplot(aes(x=prop.YO11, y=mean_Surv_to_Oct)) + 
  geom_point() +
  labs(y="Survival to Oct 2024") +
  theme_classic() 
```


### with glm

```{r}
m5 <- glm(Surv_to_Oct ~ prop.WL2+prop.CC+prop.BH+prop.WV+prop.LV1+prop.TM2+prop.SQ3+prop.DPR+prop.YO11, family = binomial, data=wl2_surv_F2_props)
summary(m5)

results5 <- c(coef(m5)[1], #intercept
             coef(m5)[2:7] + coef(m5)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results5

summary(m5)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m6 <- glm(Surv_Post_Transplant ~ prop.WL2+prop.CC+prop.BH+prop.WV+prop.LV1+prop.TM2+prop.SQ3+prop.DPR+prop.YO11, family = binomial, data=wl2_surv_F2_props)
summary(m6)

results6 <- c(coef(m6)[1], #intercept
             coef(m6)[2:7] + coef(m6)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results6

summary(m6)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m7 <- glm(Surv_to_Oct ~ Parent1, family = binomial, data=wl2_surv_F2_props)
summary(m7)

results7 <- c(coef(m7)[1], #intercept
             coef(m7)[2:7] + coef(m7)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results7

summary(m7)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m8 <- glm(Surv_to_Oct ~ Parent2, family = binomial, data=wl2_surv_F2_props)
summary(m8)

results8 <- c(coef(m8)[1], #intercept
             coef(m8)[2:7] + coef(m8)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results8

summary(m8)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m9 <- glm(Surv_to_Oct ~ Parent3, family = binomial, data=wl2_surv_F2_props)
summary(m9)

results9 <- c(coef(m9)[1], #intercept
             coef(m9)[2:7] + coef(m9)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results9

summary(m9)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m10 <- glm(Surv_to_Oct ~ Parent4, family = binomial, data=wl2_surv_F2_props)
summary(m10)

results10 <- c(coef(m10)[1], #intercept
             coef(m10)[2:7] + coef(m10)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results10

summary(m10)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m11 <- glm(Surv_Post_Transplant ~ Parent1, family = binomial, data=wl2_surv_F2_props)
summary(m11)

results11 <- c(coef(m11)[1], #intercept
             coef(m11)[2:7] + coef(m11)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results11

summary(m11)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m12 <- glm(Surv_Post_Transplant ~ Parent2, family = binomial, data=wl2_surv_F2_props)
summary(m12)

results12 <- c(coef(m12)[1], #intercept
             coef(m12)[2:7] + coef(m12)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results12

summary(m12)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m13 <- glm(Surv_Post_Transplant ~ Parent3, family = binomial, data=wl2_surv_F2_props)
summary(m13)

results13 <- c(coef(m13)[1], #intercept
             coef(m13)[2:7] + coef(m13)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results13

summary(m13)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```

```{r}
m14 <- glm(Surv_Post_Transplant ~ Parent4, family = binomial, data=wl2_surv_F2_props)
summary(m14)

results14 <- c(coef(m14)[1], #intercept
             coef(m14)[2:7] + coef(m14)[1]) %>% #coefficients + intercept
  inv_logit_scaled()
results14

summary(m14)$coefficients[,2] %>% # get the error from the summary table
  inv_logit_scaled()
```



