---
title: "WL2_Distance_Fitness"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Does climate, geographic, or genetic distance influence fitness of F1s?

-   Different relationships between distances and fitness for different life stages?

-   Similar relationships for parents and F1s with distances?

Focus on WL2, but other crosses might be interesting too

## Libraries
```{r}
library(tidyverse)
library(ggpubr) #ggarrange

sem <- function(x, na.rm=FALSE) {  #for calculating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 
```

## Read in Fitness Data
```{r}
total_fit_2024 <- read_csv("../output/WL2_Traits/WL2_2024_AllFitness.csv")
total_fit_2025 <- read_csv("../output/WL2_Traits/WL2_2025_AllFitness.csv")
```

## Read in Clim/Geo Dist Data
```{r}
clim_dist_2024 <- read_csv("../output/Climate/WL2_2024_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
clim_dist_2024_wide <- clim_dist_2024 %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop=parent.pop)

clim_dist_2025 <- read_csv("../output/Climate/WL2_2025_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
clim_dist_2025_wide <- clim_dist_2025 %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop.id=parent.pop)
```

## Figures (for now just copied and pasted from "WL2_2024_TotalFitness.Rmd", will need to edit)

### Establishment 
```{r}
WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_Establishment, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Establishment-sem_Establishment,
                    ymax=mean_Establishment+sem_Establishment), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.1600569, y= 0.4, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Establishment", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Establishment_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_Establishment, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Establishment-sem_Establishment,
                    ymax=mean_Establishment+sem_Establishment), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 0.4, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Establishment", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Establishment_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Y1 Surv
```{r}
y1_surv <- WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_Y1Surv, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Y1Surv-sem_Y1Surv,
                    ymax=mean_Y1Surv+sem_Y1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.1600569, y= 0.35, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Y1 Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Y1Surv_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_Y1Surv, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Y1Surv-sem_Y1Surv,
                    ymax=mean_Y1Surv+sem_Y1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 0.35, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Y1 Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Y1Surv_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Winter Surv
```{r}
WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_WintSurv, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_WintSurv-sem_WintSurv,
                    ymax=mean_WintSurv+sem_WintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.2, y= 1, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Winter Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_WintSurv_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_WintSurv, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_WintSurv-sem_WintSurv,
                    ymax=mean_WintSurv+sem_WintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 1, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Winter Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_WintSurv_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Surv to Bud
```{r}
WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_SurvtoBud, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_SurvtoBud-sem_SurvtoBud,
                    ymax=mean_SurvtoBud+sem_SurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.2, y= 1, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Surv to Bud Y2", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_SurvtoBud_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_SurvtoBud, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_SurvtoBud-sem_SurvtoBud,
                    ymax=mean_SurvtoBud+sem_SurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 1, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Surv to Bud Y2", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_SurvtoBud_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Prob Rep
```{r}
prob_rep <- WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_ProbFruit, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_ProbFruit-sem_ProbFruit,
                    ymax=mean_ProbFruit+sem_ProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.1600569, y= 0.13, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Probability of \n Reproducing", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_ProbFruit_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_ProbFruit, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_ProbFruit-sem_ProbFruit,
                    ymax=mean_ProbFruit+sem_ProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 0.13, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Probability of \n Reproducing", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_ProbFruit_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Figure for NSF Report
```{r}
fig_2024 <- ggarrange(y1_surv, prob_rep,
                        labels = c("A)", "B)"),  
                        font.label = list(size=30, face = "plain"), 
                        ncol=2, nrow=1) 
ggsave("../output/WL2_Traits/WL2_2024Plants_WL2Crosses_ClimDist.png", width = 26, height = 9, units = "in")
```

### Fecundity
```{r}
WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_Fecundity, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Fecundity-sem_Fecundity,
                    ymax=mean_Fecundity+sem_Fecundity), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.2, y= 17.33333, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Fruit Number", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Fecundity_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_Fecundity, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_Fecundity-sem_Fecundity,
                    ymax=mean_Fecundity+sem_Fecundity), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 38000, y= 17.33333, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Fruit Number", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_Fecundity_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

### Total Fitness
```{r}
WL2_crosses %>% 
   ggplot(aes(x=other_Parent_climdist, y=mean_TotalFitness, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_TotalFitness-sem_TotalFitness,
                    ymax=mean_TotalFitness+sem_TotalFitness), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 0.1600569, y= 2.2, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Total Fitness", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_TotalFitness_WL2Crosses_ClimDist.png", width = 12, height = 6, units = "in")

WL2_crosses %>% 
   ggplot(aes(x=other_Parent_GeoDist, y=mean_TotalFitness, 
              group = pop, colour=other_Parent_elev)) +
  geom_errorbar(aes(ymin=mean_TotalFitness-sem_TotalFitness,
                    ymax=mean_TotalFitness+sem_TotalFitness), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  annotate("text", x = 136.2622, y= 2.2, label = "WL2", 
           colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Total Fitness", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population")
ggsave("../output/WL2_Traits/WL2_2024Plants_TotalFitness_WL2Crosses_GeoDist.png", width = 12, height = 6, units = "in")
```

