---
title: "WL2_Distance_Fitness"
author: "Brandie QC"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: try pulling in F2s with a %high elev analysis?

# Does climate, geographic, or genetic distance influence fitness of F1s?

-   Different relationships between distances and fitness for different life stages: Pos geo dist effects for establishment and total fitness (total fitness not normalized) for F1s (2024 only)

-   Similar relationships for parents and F1s with distances? Opposite relationship w/ geo dit for height b/t parents and F1s for Establishment; no relats w/ distance for parents (only height) with Total Fitness 

-   Identify F1s that did well across years: Different crosses are consistent in fitness at different life stages (i.e. some good at establishment, others good at y1surv, none consistent with winter survival)

Focus on WL2, but other crosses might be interesting too

## Libraries

```{r}
library(tidyverse)
library(ggpubr) #ggarrange
library(lmerTest)

sem <- function(x, na.rm=FALSE) {  #for calculating standard error
  sd(x,na.rm=na.rm)/sqrt(length(na.omit(x)))
} 

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

## Read in Fitness Data

```{r}
total_fit_2024 <- read_csv("../output/WL2_Traits/WL2_2024_AllFitness.csv") %>% 
  mutate(num.fruit=if_else(is.na(num.fruit) | num.fruit==0, NA, num.fruit)) %>%  #make num fruit, per-capita rep output (no 0s)
  rename(FruitsY2=num.fruit)

total_fit_2025 <- read_csv("../output/WL2_Traits/WL2_2025_AllFitness.csv")  %>% 
  mutate(FruitsY1=if_else(is.na(FruitsY1) | FruitsY1==0, NA, FruitsY1),
         FruitsY2=if_else(is.na(FruitsY2) | FruitsY2==0, NA, FruitsY2),
         TotalFruit=if_else(is.na(TotalFruit) | TotalFruit==0, NA, TotalFruit)) #make num fruit, per-capita rep output (no 0s)
```

## Read in initial height data 

```{r}
init_size_2024 <- read_csv("../input/WL2_2024_Data/CorrectedCSVs/WL2_Initial_DNA_size_survey_20240607_corrected.csv")
head(init_size_2024)

pop_info_2024 <- read_csv("../input/WL2_2024_Data/Final_2023_2024_Pop_Loc_Info.csv") %>%
  select(Pop.Type:unique.ID) %>% 
  rename(row=bedrow, col=bedcol)

init_size_2024_pops <- init_size_2024 %>% 
  mutate(unique.ID=as.character(unique.ID)) %>% 
  left_join(pop_info_2024) %>% 
  mutate(unique.ID=as.numeric(unique.ID))

init_size_2024_pops %>% filter(is.na(Pop.Type)) %>% filter(!is.na(height.cm)) #2 plants with no pop info - both were not planted in field (likely died)

init_size_2024_pops %>% 
  left_join(total_fit_2024) %>% 
  ggplot(aes(x=height.cm, y=Establishment)) +
  geom_point() +
  facet_wrap(~Pop.Type)

init_size_2024_pops %>% 
  left_join(total_fit_2024) %>% 
  group_by(Pop.Type, pop) %>% 
  summarise(meanHeight=mean(height.cm, na.rm=TRUE), meanEst=mean(Establishment, na.rm=TRUE)) %>% 
  ggplot(aes(x=meanHeight, y=meanEst)) +
  geom_point() +
  facet_wrap(~Pop.Type)

#should probably account for height in models 
```

```{r}
init_size_2025 <- read_csv("../input/WL2_2025_Data/CorrectedCSVs/WL2_initial_size_DNA_corrected.csv")

pop_info_2025 <- read_csv("../input/WL2_2025_Data/2025_Pop_Loc_Info Updated.csv") %>% 
  select(status:Unique.ID) %>% 
  mutate(Pop.Type=if_else(str_detect(pop.id, "\\) x"), "F2",
                          if_else(str_detect(pop.id, "x"), "F1",
                          if_else(pop.id=="buffer" | is.na(pop.id), NA,
                                  "Parent"
                          )))) #define different pop types 

init_size_2025_pops <- init_size_2025 %>% 
  mutate(Unique.ID=as.character(Unique.ID)) %>% 
  left_join(pop_info_2025) %>% 
  mutate(Unique.ID=as.numeric(Unique.ID))
#init_size_2025_pops %>% filter(is.na(Pop.Type)) %>% filter(!is.na(height.cm))

init_size_2025_pops %>% 
  left_join(total_fit_2025) %>% 
  ggplot(aes(x=height.cm, y=WintSurv)) +
  geom_point() +
  facet_wrap(~Pop.Type)

init_size_2025_pops %>% 
  left_join(total_fit_2025) %>% 
  group_by(Pop.Type, pop.id) %>% 
  summarise(meanHeight=mean(height.cm, na.rm=TRUE), meanWintSurv=mean(WintSurv, na.rm=TRUE)) %>% 
  ggplot(aes(x=meanHeight, y=meanWintSurv)) +
  geom_point() +
  facet_wrap(~Pop.Type)
```


## Read in Clim/Geo Dist Data

```{r}
clim_dist_2024 <- read_csv("../output/Climate/WL2_2024_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
clim_dist_2024_wide <- clim_dist_2024 %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop=parent.pop)

clim_dist_2025 <- read_csv("../output/Climate/WL2_2025_Clim_Dist.csv") %>% select(-conf.low, -conf.high)
clim_dist_2025_wide <- clim_dist_2025 %>% 
  pivot_wider(names_from = timeframe, values_from = Gowers_Dist, names_prefix = "GD_") %>% 
  rename(pop.id=parent.pop)
```

## Parents & WL2 F1s Only to Start

```{r}
wl2_crosses_2024 <- total_fit_2024 %>% 
  filter(Pop.Type!="F2") %>% 
  filter(str_detect(pop, "WL2") | Pop.Type=="Parent") %>% 
  separate(pop, c("dame_pop",NA, "sire_pop"), remove = FALSE) %>% #define pops for crosses
  mutate(Other.Parent=if_else(is.na(sire_pop), dame_pop,
                              if_else(dame_pop=="WL2", sire_pop, dame_pop))) %>% 
  left_join(clim_dist_2024_wide, join_by(Other.Parent==pop))

wl2_crosses_2025 <- total_fit_2025 %>% 
  filter(Pop.Type!="F2") %>% 
  filter(str_detect(pop.id, "WL2") | Pop.Type=="Parent") %>% 
  separate(pop.id, c("dame_pop",NA, "sire_pop"), remove = FALSE) %>% #define pops for crosses
  mutate(Other.Parent=if_else(is.na(sire_pop), dame_pop,
                              if_else(dame_pop=="WL2", sire_pop, dame_pop))) %>% 
  left_join(clim_dist_2025_wide, join_by(Other.Parent==pop.id))
```

## Summaries

### WL2 F1s
```{r}
wl2_crosses_2024_summary <- wl2_crosses_2024 %>% 
  filter(str_detect(pop, "WL2")) %>% 
  group_by(Pop.Type, Other.Parent, elev_m, Geographic_Dist, GD_Recent, GD_Historic) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruitY2=mean(FruitsY2, na.rm=TRUE), semFruitY2=sem(FruitsY2, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE)) 

wl2_crosses_2025_summary <- wl2_crosses_2025 %>% 
  filter(str_detect(pop.id, "WL2")) %>% 
  group_by(Pop.Type, Other.Parent, elev_m, Geographic_Dist, GD_Recent, GD_Historic) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruitY1=mean(FruitsY1, na.rm=TRUE), semFruitY1=sem(FruitsY1, na.rm = TRUE),
            meanFruitY2=mean(FruitsY2, na.rm=TRUE), semFruitY2=sem(FruitsY2, na.rm = TRUE),
            meanTotalFruit=mean(TotalFruit, na.rm=TRUE), semTotalFruit=sem(TotalFruit, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE)) 
```

### Parents
```{r}
wl2_parents_2024_summary <- wl2_crosses_2024 %>% 
  filter(Pop.Type=="Parent") %>% 
  group_by(Pop.Type, pop, elev_m, Geographic_Dist, GD_Recent, GD_Historic) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruitY2=mean(FruitsY2, na.rm=TRUE), semFruitY2=sem(FruitsY2, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE)) 
```


### By Pop
```{r}
wl2_crosses_2024_summary2 <- wl2_crosses_2024 %>% 
  rename(pop.id=pop) %>% 
  group_by(Pop.Type, pop.id, Other.Parent, elev_m, Geographic_Dist, GD_Recent, GD_Historic) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruitY2=mean(FruitsY2, na.rm=TRUE), semFruitY2=sem(FruitsY2, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE)) %>% 
  mutate(meanTotalFruit=meanFruitY2, semTotalFruit=semFruitY2, Year="2024")

wl2_crosses_2025_summary2 <- wl2_crosses_2025 %>% 
  group_by(Pop.Type, pop.id, Other.Parent, elev_m, Geographic_Dist, GD_Recent, GD_Historic) %>% 
  summarise(meanEst=mean(Establishment, na.rm=TRUE), semEst=sem(Establishment, na.rm = TRUE),
            meanY1Surv=mean(Y1Surv, na.rm=TRUE), semY1Surv=sem(Y1Surv, na.rm = TRUE),
            meanWintSurv=mean(WintSurv, na.rm=TRUE), semWintSurv=sem(WintSurv, na.rm = TRUE),
            meanSurvtoBud=mean(SurvtoBud, na.rm=TRUE), semSurvtoBud=sem(SurvtoBud, na.rm = TRUE),
            meanFruitY1=mean(FruitsY1, na.rm=TRUE), semFruitY1=sem(FruitsY1, na.rm = TRUE),
            meanFruitY2=mean(FruitsY2, na.rm=TRUE), semFruitY2=sem(FruitsY2, na.rm = TRUE),
            meanTotalFruit=mean(TotalFruit, na.rm=TRUE), semTotalFruit=sem(TotalFruit, na.rm = TRUE),
            meanProbFruit=mean(ProbFruit, na.rm=TRUE), semProbFruit=sem(ProbFruit, na.rm = TRUE),
            meanTotalFit=mean(TotalFitness, na.rm=TRUE), semTotalFit=sem(TotalFitness, na.rm = TRUE)) %>% 
  mutate(Year="2025")

wl2_crosses_summary_all <- bind_rows(wl2_crosses_2024_summary2, wl2_crosses_2025_summary2)
```


## Figures

### Establishment

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.4, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Establishment", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Est_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.1600569, y= 0.4, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Establishment", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Est_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 0.4, label = "WL2", 
    #       colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Establishment", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Est_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_parents_2024_summary %>% 
  ggplot(aes(x=Geographic_Dist, y=meanEst, 
              group = pop, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Establishment", x="Geographic Dist", color="Elevation (m)", title="2024 Parents")
ggsave("../output/WL2_Traits/WL2_2024Plts_Est_Parents_GeoDist.png", width = 12, height = 6, units = "in")
#Potentially opposite relationship with geo dist in parents vs F1s
```


```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.4, label = "WL2", 
         #  colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Establishment", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Est_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.4, label = "WL2", 
         #  colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Establishment", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Est_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanEst, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 0.4, label = "WL2", 
        #   colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Establishment", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Est_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanEst,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanEst-semEst,
                    ymax=meanEst+semEst),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
BH x WL2 and SQ3 x WL2 have high establishment in both years

### Y1 Surv

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.35, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Y1 Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Y1Surv_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.35, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Y1 Surv", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Y1Surv_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 0.35, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Y1 Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Y1Surv_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.35, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Y1 Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Y1Surv_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.1600569, y= 0.35, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Y1 Surv", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Y1Surv_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanY1Surv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 0.35, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Y1 Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Y1Surv_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanY1Surv,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanY1Surv-semY1Surv,
                    ymax=meanY1Surv+semY1Surv),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Only TM2 x WL2 has high y1 surv in both years 

### Winter Surv

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 1, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Winter Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_WintSurv_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.2, y= 1, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Winter Surv", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_WintSurv_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 1, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Winter Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_WintSurv_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 1, label = "WL2", 
    #       colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Winter Surv", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_WintSurv_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.2, y= 1, label = "WL2", 
     #      colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Winter Surv", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_WintSurv_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanWintSurv, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 1, label = "WL2", 
 #          colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Winter Surv", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_WintSurv_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanWintSurv,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanWintSurv-semWintSurv,
                    ymax=meanWintSurv+semWintSurv),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
No crosses with consistent winter survival

### Surv to Bud

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 1, label = "WL2", 
     #      colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Surv to Bud Y2", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_SurvtoBud_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.2, y= 1, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Surv to Bud Y2", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_SurvtoBud_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 1, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Surv to Bud Y2", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_SurvtoBud_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 1, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Surv to Bud", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_SurvtoBud_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 1, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Surv to Bud", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_SurvtoBud_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanSurvtoBud, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 1, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Surv to Bud", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_SurvtoBud_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanSurvtoBud,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanSurvtoBud-semSurvtoBud,
                    ymax=meanSurvtoBud+semSurvtoBud),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Only TM2 x WL2 had data for surv to bud in both years

### Prob Rep

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.13, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Probability of \n Reproducing", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_ProbFruit_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.13, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Probability of \n Reproducing", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_ProbFruit_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 136.2622, y= 0.13, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Probability of \n Reproducing", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_ProbFruit_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.1600569, y= 0.13, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Probability of \n Reproducing", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_ProbFruit_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 0.13, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Probability of \n Reproducing", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_ProbFruit_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanProbFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 136.2622, y= 0.13, label = "WL2", 
       #    colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Probability of \n Reproducing", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_ProbFruit_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanProbFruit,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanProbFruit-semProbFruit,
                    ymax=meanProbFruit+semProbFruit),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Many crosses with consistently low prob. fruit, only TM2 x WL2 with consistent prob fruit around 20%

### Fecundity

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanFruitY2, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanFruitY2-semFruitY2,
                    ymax=meanFruitY2+semFruitY2), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 17.33333, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Fruit Number Y2", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Fec_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanFruitY2, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanFruitY2-semFruitY2,
                    ymax=meanFruitY2+semFruitY2), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.2, y= 17.33333, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Fruit Number Y2", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Fec_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanFruitY2, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanFruitY2-semFruitY2,
                    ymax=meanFruitY2+semFruitY2), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 38000, y= 17.33333, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Fruit Number Y2", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_Fec_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanTotalFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFruit-semTotalFruit,
                    ymax=meanTotalFruit+semTotalFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 17.33333, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Fruit Number", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Fec_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanTotalFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFruit-semTotalFruit,
                    ymax=meanTotalFruit+semTotalFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.2, y= 17.33333, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Fruit Number", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Fec_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanTotalFruit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFruit-semTotalFruit,
                    ymax=meanTotalFruit+semTotalFruit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 38000, y= 17.33333, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Fruit Number", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_Fec_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```
```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanTotalFruit,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanTotalFruit-semTotalFruit,
                    ymax=meanTotalFruit+semTotalFruit),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Total Fitness

```{r}
wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 2.2, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Total Fitness", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_TotalFit_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 2.2, label = "WL2", 
   #        colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Total Fitness", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_TotalFit_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2024_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 136.2622, y= 2.2, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Total Fitness", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2024 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2024Plts_TotalFit_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_parents_2024_summary %>% 
  ggplot(aes(x=Geographic_Dist, y=meanTotalFit, 
              group = pop, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Total Fitness", x="Geographic Dist", color="Elevation (m)", title="2024 Parents")

ggsave("../output/WL2_Traits/WL2_2024Plts_TotalFit_Parents_GeoDist.png", width = 12, height = 6, units = "in")
#Potentially opposite relationship with geo dist in parents vs F1s
```

```{r}
wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Recent, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
  #annotate("text", x = 0.1600569, y= 2.2, label = "WL2", 
 #          colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Total Fitness", x="Recent Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_TotalFit_WL2Cross_ClimDist_Rec.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=GD_Historic, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 0.1600569, y= 2.2, label = "WL2", 
  #         colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30)) + 
  labs(y="Avg Total Fitness", x="Historic Water Year Climate Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_TotalFit_WL2Cross_ClimDist_Hist.png", width = 12, height = 6, units = "in")

wl2_crosses_2025_summary %>% 
   ggplot(aes(x=Geographic_Dist, y=meanTotalFit, 
              group = Other.Parent, colour=elev_m)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit), width=0, linewidth = 2) +
  geom_point(size=6, aes(shape=Pop.Type)) +
 # annotate("text", x = 136.2622, y= 2.2, label = "WL2", 
     #      colour = "purple", fontface="bold", size = 22 / .pt) +
  theme_classic() + 
  scale_y_continuous(expand = c(0.01, 0.03)) +
  scale_colour_gradient(low = "#F5A540", high = "#0043F0") +
  theme(text=element_text(size=30), axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(y="Avg Total Fitness", x="Geographic Dist \n of Donor", color="Elevation \n of Donor (m)", shape="Population", title="2025 WL2 F1s")
ggsave("../output/WL2_Traits/WL2_2025Plts_TotalFit_WL2Cross_GeoDist.png", width = 12, height = 6, units = "in")
```

```{r}
wl2_crosses_summary_all %>% 
  filter(pop.id!="WL1 x WL2", pop.id!="WL2 x BH", pop.id!="WL2 x CC",
         pop.id!="WL2 x DPR", pop.id!="WL2 x LV1", pop.id!="WL2 x SQ3",
         pop.id!="WL2 x TM2", pop.id!="WL2 x WL1", pop.id!="WL2 x WV",
         pop.id!="WL2 x YO11", pop.id!="WV x WL2", pop.id!="YO11 x WL2") %>% 
  ggplot(aes(x=pop.id, y=meanTotalFit,
             group = Year, fill=Year)) +
  geom_col(width = 0.7,position = position_dodge(0.75)) +
  geom_errorbar(aes(ymin=meanTotalFit-semTotalFit,
                    ymax=meanTotalFit+semTotalFit),width=.2, 
                position =position_dodge(0.75)) +
  theme_classic() +
  scale_y_continuous(expand = c(0.01, 0)) +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Models
```{r}
wl2_crosses_2024_formod <- wl2_crosses_2024 %>% 
  filter(Pop.Type=="F1") %>% 
  left_join(init_size_2024_pops) %>% 
  mutate(across(c("GD_Recent", "GD_Historic", "Geographic_Dist", "height.cm"), scale, .names = "{.col}_scaled")) 
#wl2_crosses_2024_formod %>% filter(is.na(height.cm))

wl2_crosses_2025_formod <- wl2_crosses_2025 %>% 
  filter(Pop.Type=="F1") %>% 
  left_join(init_size_2025_pops) %>% 
  filter(!is.na(height.cm)) %>% 
  mutate(across(c("GD_Recent", "GD_Historic", "Geographic_Dist", "height.cm"), scale, .names = "{.col}_scaled"))

wl2_parents_2024_formod <- wl2_crosses_2024 %>% 
  filter(Pop.Type=="Parent") %>% 
  left_join(init_size_2024_pops) %>% 
  filter(!is.na(height.cm)) %>% 
  mutate(across(c("GD_Recent", "GD_Historic", "Geographic_Dist", "height.cm"), scale, .names = "{.col}_scaled")) 
```

### Establishment
```{r}
est_climrec <- glm(Establishment ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(est_climrec) #marginal geo dist 

est_climrec2 <- glmer(Establishment ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(est_climrec2) #marginal geo dist 

est_climhist <- glm(Establishment ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(est_climhist) #sig pos geo dist 

est_climhist2 <- glmer(Establishment ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(est_climhist2) #sig pos geo dist
```

Only a sig pos effect of geo dist in the models with historic clim distance 

```{r}
est_climrec <- glm(Establishment ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_parents_2024_formod)
summary(est_climrec) #pos clim dist, neg geo dist  

est_climrec2 <- glmer(Establishment ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_parents_2024_formod)
summary(est_climrec2) #pos clim dist, neg geo dist  

est_climhist <- glm(Establishment ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_parents_2024_formod)
summary(est_climhist) #pos clim dist, neg geo dist  

est_climhist2 <- glmer(Establishment ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_parents_2024_formod)
summary(est_climhist2) #marginal neg geo dist 
```

Opposite relationship w/ geo dist b/t parents and F1s!

### Y1 Surv
```{r}
wl2_y1surv_2024_formod <- wl2_crosses_2024_formod %>% filter(!is.na(Y1Surv))

y1surv_climrec <- glm(Y1Surv ~ GD_Recent_scaled + I(GD_Recent_scaled^2) + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_y1surv_2024_formod)
summary(y1surv_climrec) 

y1surv_climrec2 <- glmer(Y1Surv ~ GD_Recent_scaled + I(GD_Recent_scaled^2) + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_y1surv_2024_formod)
summary(y1surv_climrec2)

y1surv_climhist <- glm(Y1Surv ~ GD_Historic_scaled + I(GD_Historic_scaled^2) + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_y1surv_2024_formod)
summary(y1surv_climhist)  

y1surv_climhist2 <- glmer(Y1Surv ~ GD_Historic_scaled + I(GD_Historic_scaled^2) + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_y1surv_2024_formod)
summary(y1surv_climhist2) 
```

No sig relats b/t distances/height and y1surv

### Winter Surv
```{r}
wl2_wintersurv_2025_formod <- wl2_crosses_2025_formod %>% filter(!is.na(WintSurv))

wintersurv_climrec <- glm(WintSurv ~ GD_Recent_scaled  + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_wintersurv_2025_formod)
summary(wintersurv_climrec) 

wintersurv_climrec2 <- glmer(WintSurv ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop.id),
                     family=binomial,
                     data=wl2_wintersurv_2025_formod)
summary(wintersurv_climrec2)

wintersurv_climhist <- glm(WintSurv ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_wintersurv_2025_formod)
summary(wintersurv_climhist)  

wintersurv_climhist2 <- glmer(WintSurv ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop.id),
                     family=binomial,
                     data=wl2_wintersurv_2025_formod)
summary(wintersurv_climhist2) 
```

No sig relats b/t distances/height and wintsurv

### Prob Fruit
```{r}
probfruit_climrec <- glm(ProbFruit ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(probfruit_climrec) 

probfruit_climrec2 <- glmer(ProbFruit ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(probfruit_climrec2) 

probfruit_climhist <- glm(ProbFruit ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(probfruit_climhist) 

probfruit_climhist2 <- glmer(ProbFruit ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     family=binomial,
                     data=wl2_crosses_2024_formod)
summary(probfruit_climhist2) 
```
No sig relats b/t distances/height and prob fruit

### PerCap Fruit #
```{r}
wl2_fruits_2024_formod <- wl2_crosses_2024_formod %>% filter(!is.na(FruitsY2))

wl2_fruits_2024_formod %>% 
  ggplot(aes(FruitsY2)) +
  geom_histogram() #not normal

wl2_fruits_2024_formod %>% 
  mutate(logFruits=log(FruitsY2)) %>% 
  ggplot(aes(logFruits)) +
  geom_histogram() #not better

wl2_fruits_2024_formod %>% 
  mutate(sqrtFruits=sqrt(FruitsY2)) %>% 
  ggplot(aes(sqrtFruits)) +
  geom_histogram() #not better

fruits_climrec <- lm(FruitsY2 ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_fruits_2024_formod)
summary(fruits_climrec)

fruits_climrec2 <- lmer(FruitsY2 ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_fruits_2024_formod)
summary(fruits_climrec2) 

fruits_climhist <- lm(FruitsY2 ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_fruits_2024_formod)
summary(fruits_climhist)   

fruits_climhist2 <- lmer(FruitsY2 ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_fruits_2024_formod)
summary(fruits_climhist2) #model convergence error
```

No sig relats b/t dist/height and per cap fruit number 

### Total Fitness
```{r}
wl2_crosses_2024_formod %>% 
  ggplot(aes(TotalFitness)) +
  geom_histogram() #not normal

wl2_crosses_2024_formod %>% 
  mutate(logTotFit=log(TotalFitness)) %>% 
  ggplot(aes(logTotFit)) +
  geom_histogram() #not better

wl2_crosses_2024_formod %>% 
  mutate(sqrtTotFit=sqrt(TotalFitness)) %>% 
  ggplot(aes(sqrtTotFit)) +
  geom_histogram() #not better

totalfit_climrec <- lm(TotalFitness ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_crosses_2024_formod)
summary(totalfit_climrec) #sig pos geo dist 

totalfit_climrec2 <- lmer(TotalFitness ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_crosses_2024_formod)
summary(totalfit_climrec2) #sig pos geo dist 

totalfit_climhist <- lm(TotalFitness ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_crosses_2024_formod)
summary(totalfit_climhist) #sig pos geo dist  

totalfit_climhist2 <- lmer(TotalFitness ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_crosses_2024_formod)
summary(totalfit_climhist2) #sig pos geo dist 
```
Sig pos relat b/t geo dist and total fitness w/ caveat that Total Fitness does not have a normal distribution 

```{r}
wl2_parents_2024_formod %>% 
  ggplot(aes(TotalFitness)) +
  geom_histogram() #not normal

wl2_parents_2024_formod %>% 
  mutate(logTotFit=log(TotalFitness)) %>% 
  ggplot(aes(logTotFit)) +
  geom_histogram() #not better

wl2_parents_2024_formod %>% 
  mutate(sqrtTotFit=sqrt(TotalFitness)) %>% 
  ggplot(aes(sqrtTotFit)) +
  geom_histogram() #not better

totalfit_climrec <- lm(TotalFitness ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_parents_2024_formod)
summary(totalfit_climrec) 

totalfit_climrec2 <- lmer(TotalFitness ~ GD_Recent_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_parents_2024_formod)
summary(totalfit_climrec2) #pos height effect

totalfit_climhist <- lm(TotalFitness ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled,
                     data=wl2_parents_2024_formod)
summary(totalfit_climhist) 

totalfit_climhist2 <- lmer(TotalFitness ~ GD_Historic_scaled + Geographic_Dist_scaled + height.cm_scaled + (1|pop),
                     data=wl2_parents_2024_formod)
summary(totalfit_climhist2) #pos height effect
```

No relat w/ geo dist for parents, only height 